### 2018-07-19 paper/paper.tex
Moving to .tex

\documentclass[review=true,acmlarge]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage[linguistics]{forest}
\usepackage{tikz}
\usetikzlibrary{cd}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information
%% \acmJournal{PACMHCI}
%% \acmVolume{9}
%% \acmNumber{4}
%% \acmArticle{39}
%% \acmYear{2010}
%% \acmMonth{3}
%% \acmArticleSeq{11}

%\acmBadgeR[http://ctuning.org/ae/ppopp2016.html]{ae-logo}
%\acmBadgeL[http://ctuning.org/ae/ppopp2016.html]{ae-logo}

% Copyright
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\acmDOI{0000001.0000001}

% Paper history
%% \received{February 2007}
%% \received{March 2009}
%% \received[accepted]{June 2009}

\usepackage{amsmath}
\usepackage{listings}
\usepackage{racketlst}
\usepackage{xspace}
\lstset{basicstyle=\ttfamily,language=Racket,xleftmargin=.1\textwidth}
\usepackage{letltxmacro}
\newcommand*{\SavedLstInline}{}
\LetLtxMacro\SavedLstInline\lstinline
\DeclareRobustCommand*{\lstinline}{%
  \ifmmode
    \let\SavedBGroup\bgroup
    \def\bgroup{%
      \let\bgroup\SavedBGroup
      \hbox\bgroup
    }%
  \fi
  \SavedLstInline
}

%% To color math, put it in an \mc command, e.g., \mc{$a$}
\newcommand{\colorMATH}{black!20!blue}
\newcommand{\blue}[1] {{\color{\colorMATH} #1}}
\newcommand{\bmth}[1] {{\color{\colorMATH} $#1$}}
\newcommand{\code}[1]{\lstinline{#1}}

\newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
\newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
\newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
\newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
\newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
\newcommand{\facet}[3]{\blue{${\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}$}}

\begin{document}

\title{Racets: Embedding Policy{-}Agnostic Programming in Racket}

\author{Kristopher Micinski}
\affiliation{%
  \institution{Haverford College}
  \city{Haverford}
  \state{PA}
  \postcode{19041}
  \country{USA}}
\email{kris@cs.haverford.edu}
\author{Zhanpeng Wang}
\affiliation{%
  \institution{Haverford College}
  \city{Haverford}
  \state{PA}
  \postcode{19041}
  \country{USA}
}
\email{zwang10@haverford.edu}
\author{Thomas Gilray}
\affiliation{%
 \institution{University of Alabama}
 \city{Birmingham}
 \state{AL}
 \country{USA}}
\email{gilray@uab.edu}

\begin{abstract}lorem ipsum...\end{abstract}

%% \begin{CCSXML}
%% <ccs2012>
%%  <concept>
%%   <concept_id>10010520.10010553.10010562</concept_id>
%%   <concept_desc>Computer systems organization~Embedded systems</concept_desc>
%%   <concept_significance>500</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>10010520.10010575.10010755</concept_id>
%%   <concept_desc>Computer systems organization~Redundancy</concept_desc>
%%   <concept_significance>300</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>10010520.10010553.10010554</concept_id>
%%   <concept_desc>Computer systems organization~Robotics</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%%  <concept>
%%   <concept_id>10003033.10003083.10003095</concept_id>
%%   <concept_desc>Networks~Network reliability</concept_desc>
%%   <concept_significance>100</concept_significance>
%%  </concept>
%% </ccs2012>
%% \end{CCSXML}

%% \ccsdesc[500]{Computer systems organization~Embedded systems}
%% \ccsdesc[300]{Computer systems organization~Redundancy}
%% \ccsdesc{Computer systems organization~Robotics}
%% \ccsdesc[100]{Networks~Network reliability}

\keywords{security, faceted execution, information flow, macros}

\maketitle

\renewcommand{\shortauthors}{Micinski, Wang, and Gilray}

\section{Introduction}

As our systems become more interconnected, they consume an
ever-growing amount of data.  System designers communicate to users
how their data is used via a \emph{privacy policy}. Unfortunately,
implementing these policies correctly is challenging: users often have
partial control over the policy (e.g., whether their phone number is
publicly visible or private) and policies change frequently (e.g.,
after new laws are passed). As policies evolve, developers face
massive (re)engineering efforts to ensure that implementations match
the espoused policy.

\emph{Policy-agnostic programming} is a linguistic paradigm that
decouples the implementation of privacy policies from the code that
operates on sensitive data. This frees developers to write programs as
they would normally, without inserting logic to manage the policy
directly into application code. Instead, data is labeled with its
policy as it enters the system, and propagates through the program as
computation progresses. Policy-agnostic programming is often
implemented using faceted execution, a dynamic information-flow
monitor encoding sensitive values as \emph{facets}: decision trees
specifying different views of that data. For example, the facet
\facet{Alice}{\code{#t}}{\code{#f}} represents a value that should
appear to Alice as \code{#t} and to everyone but Alice as \blue{\code{#f}}.

Faceted execution propagates facets by extending core linguistic
primitives (such as function application). For example, consider the
application \code{(not x)} where \code{x} is
\blue{\facet{Alice}{\code{#t}}{\code{#f}}}. The programmer intends the
call to \code{not} to be operating on a \code{boolean?}, but because
\code{x} is a facet this call produces \code{#f} instead. The correct
way to interpret function application on facets is to distribute the
application through each branch, producing %% \code{m
  %% \mc{ \facet{Alice}{\code{#f}}{\code{not #t}}}}
. Other core forms
(such as \code{if}, \code{cond}, etc...) require similar changes.

The core linguistic changes required by faceted execution have led to
relatively inelegant and heavyweight implementations thusfar. For
example, Flanagan et. al (who first presented faceted execution)
extended the JavaScript runtime to account for faceted
values. Similarly, the Jeeves programming language does (what does it
do?). By contrast, Racket's highly-expressive macro system allows even
core forms (such as \code{#\%app}) to be redefined with relative ease.

In this paper we present Racets, an implementation of policy-agnostic
programming in Racket via macros. Racets provides facilities for
creating policies and faceting secure data with those policies. Racets
also extends several core forms in Racket to work with faceted
values (our implementation is detailed in Section~\ref{sec:implementation}). We
have measured the overhead of Racets in several microbenchmarks, and
have used Racets to implement a small server-based
board-game (detailed in Section~\ref{sec:evaluation}). We see Racets as a
promising prototype for policy-agnostic programming in Racket, and
conclude with several future directions in Section~\ref{sec:conclusion}.

\section{Overview of Faceted Execution}

To introduce our setting we present the implementation of Battleship,
a small guessing-based board game, in Racets (this section presents a
distilled version of our case study in
Section~\ref{sec:case-study}). In this game each player has a
grid-based board on which they place tiles (or ``ships''). The players
hide their boards from each other as play progresses in rounds. Each
turn a player guesses the position of a tile on the other player's
board. If the guess is successful that tile is removed from the
board. Play ends once one player's board has no remaining tiles, at
which point that player loses.

We implement game boards as lists of cons cells representing the
\blue{$(x,y)$} coordinates of ships. Board creation is simply the empty
list, and adding a piece is done via \lstinline|cons|:

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
(define (makeboard) '())
(define (add-piece board x y) (cons (cons x y) board))
\end{lstlisting}

Next we define \code{mark-hit}, which takes a player's board and
removes a piece if the guessed coordinate is present. We 
return a pair of the updated board and a boolean indicating
whether the guess was a hit:

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
(define (mark-hit board x y)
  (if (null? board)
      (cons board #f)
      (let* ([fst (car board)]
             [rst (cdr board)])
        (if (and (= (car fst) x)
                 (= (cdr fst) y))
            (cons rst #t)
            (let ([rst+b (mark-hit rst x y)])
              (cons (cons fst
                          (car rst+b))
                    (cdr rst+b)))))))
\end{lstlisting}

Although \code{mark-hit} will operate on sensitive data (the game
boards), it is written without any special machinery to maintain the
secrecy of \code{board}. Protecting data {w.r.t.} policies is instead handled
automatically and implicitly by a runtime monitor.
When Alice and Bob want to play a game, they both create a
\emph{label} to protect their data. A label is a predicate that takes
an argument and, if it returns true, reveals a secret. Alice's label
is used to annotate whatever data she wants to be kept
secret. Supposing Alice chooses to be player 1, she will use the
following label:

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
(define alice-label (let-label l (lambda (x) (= 1 x))) l)
\end{lstlisting}

Bob would use a similar label (but with 2 instead of 1). At runtime,
the \code{label} form creates a label \blue{$\ell_{A}$} and returns it
to the binding for \code{alice-label}. When Alice wants to protect a
value, she creates a facet annotated with her label and two
\emph{branches}. The positive (left) branch represents the value as it
should appear to her, and the negative (right) to everyone else:

\begin{lstlisting}[language=Racket,escapechar=|,name=example]
  (define alice-board
          (facet alice-label (add-pieces (makeboard) x|$_1$| y|$_1$| |$...$|) star))
\end{lstlisting}

In the above example, Alice uses \blue{$\star$} (lazy failure) to
represent that others should see nothing if they observe the data. In
other applications, she might choose a more sensible default value to
reveal to others. She may even want to create a \emph{nested}
facet. For example, in a social-networking application she may want a
nested facet consisting of two labels for
\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. She
would present three views of her social-media profile: \bmth{p_1} to
her family, containing her phone number and other contact information,
\bmth{p_2} to her friends showing her interests, and \bmth{p_3} to
everyone else, showing only her name and email.

\begingroup
\begin{gather*}
\pgfkeys{/pgf/inner sep=0pt} \pgfkeys{/pgf/inner xsep=0pt}
  \begin{forest}
    l sep=0,s sep=1em,
    for children={l sep=0,s sep=1em},
    [\bmth{\ell_{\text{Family}}} [\bmth{p_1}] [\bmth{\ell_{\text{Friends}}} [\bmth{p_2}] [\bmth{p_3}]]]
  \end{forest}
\end{gather*}
\endgroup

As play of the game progresses, Alice and Bob both make guesses, and a
driver calls the function \code{mark-hit} with each of their (faceted)
game boards. However, because Alice and Bob's game boards are both
facets, \code{mark-hit} cannot be immediately applied, as the argument
\code{board} is a facet. Faceted execution ``splits'' the execution of
the function on faceted arguments, running it first on the positive
branch, then again on the negative branch. Finally, the results of
each branch are merged to produce a facet:

%% \begin{center}
%%   \begin{tikzpicture}
%% 	  \node (0) at (0, 1) {\lstinline|(mark-hit |{\color{\colorMATH}\(\facet{\ell_A}{v^+}{v^-} ~~ x ~~y\)}\lstinline|)|};
%% 	  \node (1) at (2, 0)  {\lstinline|(mark-hit |{\color{\colorMATH}\(v^- ~~ x ~~ y\)}\lstinline|)|{\color{\colorMATH}\(~~= v''\)}};
%% 	  \node (2) at (-2, 0) {\lstinline|(mark-hit |{\color{\colorMATH}\(v^+ ~~ x ~~ y\)}\lstinline|)|{\color{\colorMATH}\(~~= v'\)}};
%% 	  \node (3) at (0, -1) {{\color{\colorMATH}\(\facet{\ell_A}{v'}{v''}\)}};
%% 	  \draw [->] (0) edge (1);
%% 	  \draw [->] (0) edge (2);
%% 	  \draw [->] (1) edge (3);
%% 	  \draw [->] (2) edge (3);
%%   \end{tikzpicture}
%% \end{center}

Because the applied function could be stateful, faceted execution also
records the current privilege level in a \emph{program counter}. The
program counter is used to build facets when writes are made to the
store inside of a privileged context. We expand upon these subtleties
in Section~\ref{sec:semantics}, where we present a full semantics for
faceted execution.

\kris{Stuff about obs here..}

\bibliographystyle{ACM-Reference-Format}
\bibliography{paper}

\end{document}

### 2018-07-19 paper/paper.tex
adding more semantics stuff..

@@
 \usetikzlibrary{cd}
-
+\usepackage{xcolor}
+\usepackage{mathpartir} % Inference rules
 \usepackage[ruled]{algorithm2e} % For algorithms
@@
 \newcommand{\colorMATH}{black!20!blue}
+\newcommand{\colorFAC}{black!20!red}
 \newcommand{\blue}[1] {{\color{\colorMATH} #1}}
+\newcommand{\fcol}[1] {{\color{\colorFAC} #1}}
 \newcommand{\bmth}[1] {{\color{\colorMATH} $#1$}}
@@
 \newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
-\newcommand{\facet}[3]{\blue{${\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}$}}
+\newcommand{\facet}[3]{{\fcol{\ensuremath{\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}}}}
+\newcommand{\formfacet}[3]{{\fcol{\ensuremath{\langle \langle \, {#1} \: ? \: {#2} \diamond \: {#3} \,  \rangle \rangle}}}}
 
@@
 
+\section{A Formal Semantics for Faceted Execution}
+
+\begin{figure}
+\begin{displaymath}
+  \begin{array}{lcrcl}
+    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{\#t} \mid \code{\#f} \mid \ldots} \\
+    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \blue{\ldots}  \\
+    \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
+    & & & \blue{\mid} & \blue{(\lambda ~ (x) ~ e) \mid (e ~ e)} \\
+    & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
+    & & & \blue{\mid} & \blue{(\code{let-label} ~ \ell ~ e ~ e)} \\
+    & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\
+    & & & \blue{\mid} & \blue{(\code{obs} ~ e ~ e ~ e)} \\
+  \end{array}
+\end{displaymath}
+\label{fig:syntax}
+\caption{Syntax of \lang}
+\end{figure}
+
+We now present a semantics for a core language (\lang) which includes
+facets. Our presentation largely mirrors that of Austin et
+al.~\cite{Austin:2013}. The syntax of our language---reminiscent of
+Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
+calculus with references (which have interact with facets in a subtle
+way) and three forms unique to faceted execution: label creation,
+facet construction, and facet observation.
+
+\begin{figure*}
+    \begin{tabular}{cc}
+      \begin{minipage}{.5\textwidth}
+        \begin{displaymath}
+          \begin{array}{rcrcl}
+            \blue{\alpha} & \blue{\in} & \blue{\text{addr}} & \blue{=} & \blue{\ldots} \\
+            \blue{bv} & \blue{\in} & \blue{\text{base-val}} & \blue{::=} & \blue{c \mid \alpha \mid \langle \lambda x.~ e, \rho \rangle \mid \star}\\
+            \fcol{v} & \blue{\in} & \blue{\text{faceted-val}} & \blue{::=} & \blue{bv \mid} ~ \fcol{\facet{\blue{\alpha}}{v}{v}}
+            \\
+          \end{array}
+        \end{displaymath}
+      \end{minipage}
+      &
+      \begin{minipage}{.5\textwidth}
+        \begin{displaymath}
+          \begin{array}{rcrcl}
+            \blue{\alpha} & \blue{\in} & \blue{\text{addr}} & \blue{=} & \blue{\ldots} \\
+            \blue{bv} & \blue{\in} & \blue{\text{base-val}} & \blue{::=} & \blue{c \mid \alpha \mid \langle \lambda x.~ e, \rho \rangle \mid \star}\\
+            \blue{fv} & \blue{\in} & \blue{\text{facet-val}} & \blue{::=} & %% \blue{bv \mid \facet{\alpha}{fv}{fv}}
+            \\
+          \end{array}
+        \end{displaymath}
+      \end{minipage}
+    \end{tabular}
+    \\
+    \hfill \boxed{\blue{e, \rho, \sigma \Downarrow_{pc}^E \sigma, v}}
+    \\
+    \begingroup
+    \color{\colorMATH}
+    \begin{displaymath}
+      \begin{array}{c}
+        \begin{array}{cccc}
+          \inferrule[\textsc{Const}]{ }
+                    {c, \rho, \sigma \Downarrow_{pc}^E \sigma, c}
+                    & 
+                    \inferrule[\textsc{Var}]{ }
+                              {x, \rho, \sigma \Downarrow_{pc}^E \sigma, \rho(x)}
+                              & 
+                              \inferrule[\textsc{Lambda}]{ }
+                                        {\lambda x. ~ e, \rho, \sigma \Downarrow_{pc}^E \sigma, \langle \lambda x. ~ e, \rho \rangle}
+                                        &
+        \end{array}
+        \\
+        \begin{array}{ccc}
+          \inferrule[\textsc{Box}]
+                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
+                      \alpha \not\in dom(\sigma') \\\\
+                      \sigma'' = \sigma' [\alpha \mapsto \formfacet{pc}{v}{\star}]}
+                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E v, \sigma''}
+                    & 
+          \inferrule[\textsc{Unbox}]
+                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
+                     v' = \fcol{read(\sigma',v,pc)}}
+                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E v', \sigma'}
+                    & 
+          \inferrule[\textsc{Set}]
+                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \\\\
+                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
+                     \sigma''' = \fcol{write(\sigma'', v_1, pc, v_2)}}
+                    {(\code{set!} ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v_2}
+        \end{array}
+        \\
+        \begin{array}{ccc}
+          {\color{\colorFAC}
+          \inferrule[\textsc{Let-Label}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v \\\\
+           \alpha \not\in dom(\sigma) \and \sigma' = \sigma [\alpha \mapsto v] \\\\
+           e_2, \rho [ \ell \mapsto \alpha ], \sigma' \Downarrow_{pc}^E \sigma'', v'}
+          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma'', v'}}
+          & 
+          {\color{\colorFAC}
+          \inferrule[\textsc{Fac-Create}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', l \\\\
+           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
+           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 }
+          {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', \formfacet{pc}{v_1}{v_2}}}
+          & 
+          {\color{\colorFAC}
+          \inferrule[\textsc{Obs}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \\\\
+           e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v  \\\\
+           \langle (\lambda x.~e), \rho' \rangle = \sigma''(\ell) \\\\
+           e_3, \rho' [x \mapsto v], \sigma'' \Downarrow_{pc}^E \sigma''', v'}
+          {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''' v'}}
+        \end{array}
+      \end{array}
+    \end{displaymath}
+              %%\inferrule[]
+    \endgroup
+\end{figure*}
+
 \bibliographystyle{ACM-Reference-Format}

### 2018-07-20 paper/paper.tex
Adding formalization section math, mostly done now, but no prose, going to work on section 4 tonight
hacking on section 4

@@
 \usepackage[ruled]{algorithm2e} % For algorithms
+\usepackage{setspace}
 \renewcommand{\algorithmcfname}{ALGORITHM}
@@
 \newcommand{\formfacet}[3]{{\fcol{\ensuremath{\langle \langle \, {#1} \: ? \: {#2} \diamond \: {#3} \,  \rangle \rangle}}}}
+\newcommand{\var}[1]{\mathit{#1}}
 
@@
           \begin{array}{rcrcl}
-            \blue{\alpha} & \blue{\in} & \blue{\text{addr}} & \blue{=} & \blue{\ldots} \\
-            \blue{bv} & \blue{\in} & \blue{\text{base-val}} & \blue{::=} & \blue{c \mid \alpha \mid \langle \lambda x.~ e, \rho \rangle \mid \star}\\
-            \blue{fv} & \blue{\in} & \blue{\text{facet-val}} & \blue{::=} & %% \blue{bv \mid \facet{\alpha}{fv}{fv}}
+            \fcol{b} & \fcol{\in} & \fcol{\text{branch}} & \fcol{::=} & \fcol{+ \ell \mid - \ell} \\
+            \fcol{pc} & \fcol{\in} & \fcol{\text{PC}} & \fcol{=} & \fcol{\wp(\text{branch})} \\
+            \blue{\rho} & \blue{\in} & \blue{\text{env}} & \blue{=} & \blue{\text{var} \rightharpoonup v}\\
+            \blue{\sigma} & \blue{\in} & \blue{\text{store}} & \blue{=} & \blue{\text{addr} \rightharpoonup v}
             \\
@@
     \\
-    \hfill \boxed{\blue{e, \rho, \sigma \Downarrow_{pc}^E \sigma, v}}
+    \hfill \textit{(Expression Evaluation)} \boxed{\blue{e, \rho, \sigma \Downarrow_{pc}^E \sigma, v}}
     \\
+    \begin{displaymath}
+      \begin{array}{c}
         \begingroup
         \color{\colorMATH}
-    \begin{displaymath}
-      \begin{array}{c}
         \begin{array}{cccc}
@@
                     &
+          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
+                                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
+                                     \fcol{(v_1 v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}
+                                    {(e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v'}
         \end{array}
+       \endgroup
         \\
+        \begingroup
+        \color{\colorMATH}
         \begin{array}{ccc}
           \inferrule[\textsc{Box}]
-                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
+                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \and
                       \alpha \not\in dom(\sigma') \\\\
@@
                     {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
-                     v' = \fcol{read(\sigma',v,pc)}}
+                     v' = \fcol{\var{read}(\sigma',v,pc)}}
                     {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E v', \sigma'}
@@
           \inferrule[\textsc{Set}]
-                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \\\\
+                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
                      e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
-                     \sigma''' = \fcol{write(\sigma'', v_1, pc, v_2)}}
+                     \sigma''' = \fcol{\var{write}(\sigma'', v_1, pc, v_2)}}
                     {(\code{set!} ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v_2}
         \end{array}
+       \endgroup
+       \\
+       \hfill \textit{(Facet Creation)}
        \\
@@
           {\color{\colorFAC}
-          \inferrule[\textsc{Let-Label}]
-          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v \\\\
-           \alpha \not\in dom(\sigma) \and \sigma' = \sigma [\alpha \mapsto v] \\\\
-           e_2, \rho [ \ell \mapsto \alpha ], \sigma' \Downarrow_{pc}^E \sigma'', v'}
-          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma'', v'}}
+          \inferrule[\textsc{Fac-Create-Split}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+            \{+\ell, -\ell\} \cup pc = \varnothing \\\\
+           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
+           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
+           v = \formfacet{pc}{v_1}{v_2}}
+          {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
           & 
           {\color{\colorFAC}
-          \inferrule[\textsc{Fac-Create}]
-          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', l \\\\
-           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
-           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 }
-          {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', \formfacet{pc}{v_1}{v_2}}}
+          \inferrule[\textsc{Fac-Create-Left}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+           + \ell \in pc \\\\
+           e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
+          {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
+          & 
+          {\color{\colorFAC}
+          \inferrule[\textsc{Fac-Create-Right}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+           - \ell \in pc \\\\
+           e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
+          {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}     \end{array}
+
+      \end{array}
+    \end{displaymath}
+    \\
+    \hfill \textit{(Label Creation / Observation)}
+    \\
+    \[
+    \begin{array}{cc}
+      {\color{\colorFAC}
+        \inferrule[\textsc{Let-Label}]
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \langle \lambda x. ~ e, \rho' \rangle \\\\
+           \alpha \not\in dom(\sigma') \and \sigma'' = \sigma' [\alpha \mapsto \langle \lambda x. ~ e, \rho' \rangle] \\\\
+           e_2, \rho [ \ell \mapsto \alpha ], \sigma'' \Downarrow_{pc}^E \sigma''', v}
+          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
           & 
@@
           \inferrule[\textsc{Obs}]
-          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \\\\
-           e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v  \\\\
+                    {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell
+                      \and e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v  \\\\
                       \langle (\lambda x.~e), \rho' \rangle = \sigma''(\ell) \\\\
-           e_3, \rho' [x \mapsto v], \sigma'' \Downarrow_{pc}^E \sigma''', v'}
-          {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''' v'}}
+                      e, \rho' [x \mapsto v], \sigma'' \Downarrow_{pc}^E \sigma''', v^{\pm} \\\\
+                      e_3, \rho, \sigma''' \Downarrow_{pc}^E \sigma'''', v' \\\\
+                      v'' = \fcol{\var{obs}(\ell, pc, v', v^{\pm})}}
+                    {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'''', v''}}
+    \end{array}
+    \]
+    \\
+    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
+    \\
+    \begingroup
+    \color{\colorMATH}
+    \begin{displaymath}
+      \begin{array}{c}
+        \begin{array}{ccc}
+          {\color{\colorMATH}
+          \inferrule[\textsc{App-$\star$}]
+          { }
+          {(\star ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, \star}}
+          & 
+          {\color{\colorMATH}
+          \inferrule[\textsc{App-Base}]
+          {e, \rho'[x \mapsto v], \sigma \Downarrow_{pc}^E \sigma', v' }
+          {(\langle \lambda x.~e, \rho' \rangle ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
+          & 
+          {\color{\colorFAC}
+          \inferrule[\textsc{App-Split}]
+          {\{+\ell, -\ell\} \cap pc = \varnothing \and
+            (v^+ ~ v), \rho, \sigma \Downarrow_{pc \cup \{+\ell\}}^A \sigma', {v^+}' \\\\
+            (v^- ~ v), \rho, \sigma' \Downarrow_{pc \cup \{-\ell\}}^A \sigma'', {v^-}' \and
+            v' = \formfacet{\{+ \ell\}}{{v^+}'}{{v^-}'}}
+          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma'', v'}}
+        \end{array}
+        \\
+        \begin{array}{cc}
+          {\color{\colorFAC}
+          \inferrule[\textsc{App-Facet-Pos}]
+          {+\ell \in pc \\\\
+            (v^+ ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}
+          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
+          & 
+          {\color{\colorFAC}
+          \inferrule[\textsc{App-Facet-Neg}]
+          {-\ell \in pc \\\\
+            (v^- ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}
+          {(\facet{\ell}{v^+}{v^-} ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma', v'}}
         \end{array}
@@
     \endgroup
+    \label{fig:semantics}
 \end{figure*}
+
+\section{Faceted Execution as Macros}
+
+The semantics of faceted execution is an extension of the lambda
+calculus, leading to a natural question: can we use Racket's macros to
+extend Racket to faceted execution? We will see that the answer is
+yes, and the translation from the big-step rules is surprisingly
+straightforward. This section of our paper describes the design of
+Racets, a prototype implementation of faceted execution using Racket
+macros. In Section~\ref{sec:conclusion} we remark upon current
+directions scaling Racets to the whole of Racket.
+
+\paragraph*{Choosing a Representation for Facets, Labels, and Program Counters}
+
+In setting out to implement facets, we must first choose how we will
+represent facets, labels, and program counters. We have chosen to
+implement facets simply as Racket \lstinline|struct|s, containing a
+label along with positive and negative branches:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+(struct facet (labelname left right))
+\end{lstlisting}
+
+Next, we must choose a representation of labels. At first
+consideration, it appears sensible to represent labels simply as
+closures. After all, labels are simply used as predicates testing
+whether or not to reveal a facet's positive or negative
+branch. However, there is a subtle issue: facet canonicalization
+relies upon a total order for labels. In light of this, we represent
+labels as a pair of a name and a policy:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+(struct labelpair (name pol))
+\end{lstlisting}
+
+Now that we have defined labels, we can define branches, which are
+positive or negative labels:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+(struct pos (lab))
+(struct neg (lab))
+\end{lstlisting}
+
+Similarly, program counters are sets of branches. However, we must
+still ask how we will keep track of the ``current'' program
+counter. Our implementation uses Racket's parameters, though other
+mechanisms (such as continuation marks\kris{cite}, to which parameters
+macro-expand) could also be used. Racets defines the parameter
+\code{current-pc}, and updates it as computation progresses:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+(define current-pc (make-parameter (set)))
+\end{lstlisting}
+
+\paragraph*{Facet Creation}
+
+Facet creation appears as three separate rules in
+Figure~\ref{fig:semantics}, which we recapitulate here in three
+distint colors for each case:
+
+\[
+\begin{array}{ccc}
+  {\color{brown}
+    \inferrule[\textsc{Fac-Create-Left}]
+              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+                \boxed{+ \ell \in pc} \\\\
+                e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
+              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
+  & 
+  {\color{gray}
+    \inferrule[\textsc{Fac-Create-Right}]
+              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+                \boxed{- \ell \in pc} \\\\
+                e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
+              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
+  &
+  {\color{purple}
+    \inferrule[\textsc{Fac-Create-Split}]
+              {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+                \boxed{\{+\ell, -\ell\} \cup pc = \varnothing} \\\\
+                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
+                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
+                v = \formfacet{pc}{v_1}{v_2}}
+              {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
+
+\end{array}
+\]
+
+Translating these rules to Racket involves observing that each of
+these rules will apply under one of three disjoint circumstances (each
+of them boxed in the above rules): $+\ell \in pc$, $-\ell \in pc$, or
+else $\{+\ell,-\ell\} \cap pc = \varnothing$. This leads to a
+relatively straightforward implementation that inspects the current
+program counter to decide which rule to implement:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+(define-syntax-rule (fac l e1 e2)
+  (cond
+|{\color{brown}|    [(set-member? (current-pc) (pos (facet-labelname l))) e1] |}|
+|{\color{gray}|    [(set-member? (current-pc) (neg (facet-labelname l))) e2]  |}|
+
+|{\color{purple}|    [else
+     (let ([left
+            (parameterize ([current-pc (set-add (current-pc)
+                                                (pos (facet-labelname l)))]))]
+           [right
+            (parameterize ([current-pc (set-add (current-pc)
+                                                (neg (facet-labelname l)))]))]
+           (mkfacet (labelpair-name l) v1 v2)))])) |}|
+\end{lstlisting}
+
+As our definition is a transliteration of that in Figure 6 of Austin
+et. al's paper~\cite{Austin:2012}, we omit the implementation here.
+The result is a function, \code{mkfacet}, which (given a label and
+both positive and negative branches) forms a facet:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+(define (mkfacet label v1 v2)
+  (canonicalize (set-add (current-pc) (pos name)) v1 v2))
+\end{lstlisting}
 

### 2018-07-20 paper/paper.tex
fix stuffs on Sec 3 semantics. Need to fix the format of Sec 3.

@@
                     &
-          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
-                                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
-                                     \fcol{(v_1 v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}
+          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v_1 \and
+                                     e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v_2 \\\\
+                                     \fcol{(v_1 ~ v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}
                                     {(e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v'}
@@
        \endgroup
-        \\
+        \\\\
         \begingroup
@@
           \inferrule[\textsc{Box}]
-                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \and
+                    {e, \rho, \sigma \Downarrow_{pc}^E \sigma', v \and
                       \alpha \not\in dom(\sigma') \\\\
                       \sigma'' = \sigma' [\alpha \mapsto \formfacet{pc}{v}{\star}]}
-                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E v, \sigma''}
+                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E \sigma'', \alpha}
                     & 
           \inferrule[\textsc{Unbox}]
-                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
+                    {e, \rho, \sigma \Downarrow_{pc}^E \sigma', v \\\\
                      v' = \fcol{\var{read}(\sigma',v,pc)}}
-                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E v', \sigma'}
+                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E \sigma', v'}
                     & 
           \inferrule[\textsc{Set}]
-                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
-                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
+                    {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v_1 \and
+                     e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v_2 \\\\
                      \sigma''' = \fcol{\var{write}(\sigma'', v_1, pc, v_2)}}
@@
        \endgroup
-       \\
+       \\\\
        \hfill \textit{(Facet Creation)}
@@
           {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
-            \{+\ell, -\ell\} \cup pc = \varnothing \\\\
+            \{+\ell, -\ell\} \cap pc = \varnothing \\\\
            e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
@@
           {\color{\colorFAC}
-          \inferrule[\textsc{Fac-Create-Left}]
+          \inferrule[\textsc{Fac-Create-Pos}]
           {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
            + \ell \in pc \\\\
-           e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
+           e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v}
           {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
@@
           {\color{\colorFAC}
-          \inferrule[\textsc{Fac-Create-Right}]
+          \inferrule[\textsc{Fac-Create-Neg}]
           {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
            - \ell \in pc \\\\
-           e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
+           e_3, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v}
           {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}     \end{array}
@@
                       e_3, \rho, \sigma''' \Downarrow_{pc}^E \sigma'''', v' \\\\
-                      v'' = \fcol{\var{obs}(\ell, pc, v', v^{\pm})}}
+                      v'' = \fcol{\var{obs}(\ell, v', v^{\pm})}}
                     {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'''', v''}}
@@
     \\
-    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
+    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v_1 ~ v_2), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
     \\
@@
         \begin{array}{cc}
+        \\\\
           {\color{\colorFAC}
@@
         \end{array}
+      \end{array}
+    \end{displaymath}
+    \\
+    \newpage
+    \hfill \textit{(Metafunctions)}
+    \\
+    \begin{displaymath}
+      \begin{array}{rclrr}
+        {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
+        {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
+        {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
+        {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
+      \end{array}
+    \end{displaymath}
+    \begin{displaymath}
+      \begin{array}{rclrr}
+        {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
+        {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
+        & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
+      \end{array}
+    \end{displaymath}
+    \begin{displaymath}
+      \begin{array}{rclrr}
+        {obs(\ell, b, bv)} & {=} & {bv} & & \\
+        {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
+        {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
+        {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
       \end{array}

### 2018-07-20 paper/paper.tex
fix the format of Sec 3 semantics.

--- 2018-07-20 paper/paper.tex
@@
     \end{displaymath}
-              %%\inferrule[]
     \endgroup
     \label{fig:semantics}
+\end{figure*}
+
+\begin{figure*}
+  \hfill \textit{(Metafunctions)}
+      \\
+      \begin{displaymath}
+        \begin{array}{rclrr}
+          {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
+          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
+          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
+          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
+        \end{array}
+      \end{displaymath}
+      \\
+      \begin{displaymath}
+        \begin{array}{rclrr}
+          {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
+          {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
+          & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
+        \end{array}
+      \end{displaymath}
+      \\
+      \begin{displaymath}
+        \begin{array}{rclrr}
+          {obs(\ell, b, bv)} & {=} & {bv} & & \\
+          {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
+          {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
+          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
+        \end{array}
+      \end{displaymath}
 \end{figure*}

### 2018-07-20 paper/paper.tex
the format of Sec3 semantics is fixed. Semantics should be all set now

@@
           {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
-          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
+          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = & \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
         \end{array}

### 2018-07-20 paper/paper.tex
will add more prose to sec3 later tonight

@@
 way to interpret function application on facets is to distribute the
-application through each branch, producing %% \code{m
+application through each branch, producing \zw{producing ...?} %% \code{m
   %% \mc{ \facet{Alice}{\code{#f}}{\code{not #t}}}}
@@
 values. Similarly, the Jeeves programming language does (what does it
-do?). By contrast, Racket's highly-expressive macro system allows even
+do?)\zw{Need to complete this sentence}. By contrast, Racket's 
+highly-expressive macro system allows even
 core forms (such as \code{#\%app}) to be redefined with relative ease.
@@
 calculus with references (which have interact with facets in a subtle
-way) and three forms unique to faceted execution: label creation,
-facet construction, and facet observation.
+way) and three forms unique to faceted execution: facet construction, 
+label creation, and facet observation.
+
+\zw{Facet construction allows the users to construct a facet value that
+consists of a policy, a private/positive variable that can be a basic value
+or another facet value but is hidden away from other users, and a public/negative 
+variable. }
+
+\zw{Label creation dynamically creates a label binding to a given policy.
+A policy consists of a policy variable and a policy body/expression. 
+When a lable is invoked in the faceted executions, the policy will be called
+to evaluate the given faceted value. When the policy is invoked, the policy
+body (e.g. lambda function) evaluates to a boolean, which indicates whether
+to observe the positive or the negative branch of a faceted value. This allows
+the users to protect their data via choosing what data to be seen by others and 
+hiding the sensitive data.}
+
+\zw{Facet observation }
 

### 2018-07-20 paper/paper.tex
partial work on 4

--- 2018-07-20 paper/paper.tex
@@
 \usepackage{xspace}
-\lstset{basicstyle=\ttfamily,language=Racket,xleftmargin=.1\textwidth}
+\lstset{language=Racket,xleftmargin=.1\textwidth,escapeinside={<@}{@>}}
 \usepackage{letltxmacro}
@@
 \section{A Formal Semantics for Faceted Execution}
+\label{sec:semantics}
 
@@
                     &
-          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v_1 \and
-                                     e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v_2 \\\\
-                                     \fcol{(v_1 ~ v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}
+          \inferrule[\textsc{Apply}]{e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
+                                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
+                                     \fcol{(v_1 v_2), \rho, \sigma'' \Downarrow_{pc}^A \sigma''', v'}}
                                     {(e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v'}
@@
        \endgroup
-        \\\\
+        \\
         \begingroup
@@
           \inferrule[\textsc{Box}]
-                    {e, \rho, \sigma \Downarrow_{pc}^E \sigma', v \and
+                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \and
                       \alpha \not\in dom(\sigma') \\\\
                       \sigma'' = \sigma' [\alpha \mapsto \formfacet{pc}{v}{\star}]}
-                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E \sigma'', \alpha}
+                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E v, \sigma''}
                     & 
           \inferrule[\textsc{Unbox}]
-                    {e, \rho, \sigma \Downarrow_{pc}^E \sigma', v \\\\
+                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
                      v' = \fcol{\var{read}(\sigma',v,pc)}}
-                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E \sigma', v'}
+                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E v', \sigma'}
                     & 
           \inferrule[\textsc{Set}]
-                    {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v_1 \and
-                     e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v_2 \\\\
+                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \and
+                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
                      \sigma''' = \fcol{\var{write}(\sigma'', v_1, pc, v_2)}}
@@
        \endgroup
-       \\\\
+       \\
        \hfill \textit{(Facet Creation)}
@@
           {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
-            \{+\ell, -\ell\} \cap pc = \varnothing \\\\
+            \{+\ell, -\ell\} \cup pc = \varnothing \\\\
            e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
@@
           {\color{\colorFAC}
-          \inferrule[\textsc{Fac-Create-Pos}]
+          \inferrule[\textsc{Fac-Create-Left}]
           {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
            + \ell \in pc \\\\
-           e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v}
+           e_2, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
           {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}
@@
           {\color{\colorFAC}
-          \inferrule[\textsc{Fac-Create-Neg}]
+          \inferrule[\textsc{Fac-Create-Right}]
           {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
            - \ell \in pc \\\\
-           e_3, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v}
+           e_3, \rho, \sigma \Downarrow_{pc}^E \sigma'', v}
           {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'', v}}     \end{array}
@@
                       e_3, \rho, \sigma''' \Downarrow_{pc}^E \sigma'''', v' \\\\
-                      v'' = \fcol{\var{obs}(\ell, v', v^{\pm})}}
+                      v'' = \fcol{\var{obs}(\ell, pc, v', v^{\pm})}}
                     {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma'''', v''}}
@@
     \\
-    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v_1 ~ v_2), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
+    \hfill \textit{(Possibly-Faceted Application)} \boxed{\fcol{(v ~ v), \rho, \sigma \Downarrow_{pc}^A \sigma, v}}
     \\
@@
         \begin{array}{cc}
-        \\\\
           {\color{\colorFAC}
@@
     \end{displaymath}
+              %%\inferrule[]
     \endgroup
     \label{fig:semantics}
-\end{figure*}
-
-\begin{figure*}
-  \hfill \textit{(Metafunctions)}
-      \\
-      \begin{displaymath}
-        \begin{array}{rclrr}
-          {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
-          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
-          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
-          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
-        \end{array}
-      \end{displaymath}
-      \\
-      \begin{displaymath}
-        \begin{array}{rclrr}
-          {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
-          {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
-          & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
-        \end{array}
-      \end{displaymath}
-      \\
-      \begin{displaymath}
-        \begin{array}{rclrr}
-          {obs(\ell, b, bv)} & {=} & {bv} & & \\
-          {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
-          {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
-          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
-        \end{array}
-      \end{displaymath}
 \end{figure*}
@@
 
-\[
+\[\small
 \begin{array}{ccc}
   {\color{brown}
-    \inferrule[\textsc{Fac-Create-Left}]
+    \inferrule[\textsc{Fac-Create-Pos}]
               {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
@@
   {\color{gray}
-    \inferrule[\textsc{Fac-Create-Right}]
+    \inferrule[\textsc{Fac-Create-Neg}]
               {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
@@
 
-Translating these rules to Racket involves observing that each of
-these rules will apply under one of three disjoint circumstances (each
-of them boxed in the above rules): $+\ell \in pc$, $-\ell \in pc$, or
-else $\{+\ell,-\ell\} \cap pc = \varnothing$. This leads to a
-relatively straightforward implementation that inspects the current
-program counter to decide which rule to implement:
+Translating these rules to Racket involves observing that each one
+will apply under one of three disjoint circumstances (each of them
+boxed in the above rules): \bmth{+\ell \in pc}, \bmth{-\ell \in pc},
+or else \bmth{\{+\ell,-\ell\} \cap pc = \varnothing}. This is a common
+idiom in our faceted semantics, as we often want to select the
+appropriate branch of a facet if its label already exists in
+\bmth{pc}.
 
-\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
+At first glance, it may not be obvious that we even \emph{need} a maco
+for facet creation. But according to our semantics, the following
+snippet should produce \code{#t} if \bmth{+\ell \in pc}:
+
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=other,numbers=none]
+(fac l #t (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
+\end{lstlisting}
+
+If we were to implement \code{fac} as a function, it would force
+evaluation of the negative branch, inconsistent with the semantics of
+\textsc{Fac-Create-Pos}. We can implement each of these conditions as
+a Racket macro by considering whether \bmth{\ell \in pc}, as shown in
+Figure~\ref{fig:fac-create}. Each color in the listing corresponds to
+the analogous semantic rule. The implementation of
+\textsc{Fac-Create-Pos} and \textsc{Fac-Create-Neg} is relatively
+straightforward, but \textsc{Fac-Create-Split} extends \bmth{pc} for
+each branch and subsequently forms a facet. This function implements
+canonicalizing facet construction, and (as the implementation is a
+transliteration of that in Figure 6 of Austin et
+al.~\cite{Austin:2012}) we omit its definition here.
+
+\begin{figure}
+{\small
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
 (define-syntax-rule (fac l e1 e2)
   (cond
-|{\color{brown}|    [(set-member? (current-pc) (pos (facet-labelname l))) e1] |}|
-|{\color{gray}|    [(set-member? (current-pc) (neg (facet-labelname l))) e2]  |}|
+\end{lstlisting}
+\vspace{-.7\baselineskip}
+{\color{brown}
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{brown}]
+    [(set-member? (current-pc) (pos (facet-labelname l))) e1]
+\end{lstlisting}
+}
+\vspace{-.7\baselineskip}
+{\color{gray}
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{gray}]
+    [(set-member? (current-pc) (neg (facet-labelname l))) e2]
+\end{lstlisting}
+}
+\vspace{-.7\baselineskip}
+{\small\color{purple}
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets,identifierstyle=\color{purple},keywordstyle=\color{purple}]
+    [else
+     (let ([left (parameterize
+                     ([current-pc (set-add (current-pc)
+                                           (pos (facet-labelname l)))]))]
+           [right (parameterize
+                      ([current-pc (set-add (current-pc)
+                                            (neg (facet-labelname l)))]))]
+           (mkfacet (labelpair-name l) v1 v2)))]))
+\end{lstlisting}}
+\caption{Facet creation as a macro}
+\label{fig:fac-create}
+\end{figure}
 
-|{\color{purple}|    [else
-     (let ([left
-            (parameterize ([current-pc (set-add (current-pc)
-                                                (pos (facet-labelname l)))]))]
-           [right
-            (parameterize ([current-pc (set-add (current-pc)
-                                                (neg (facet-labelname l)))]))]
-           (mkfacet (labelpair-name l) v1 v2)))])) |}|
+\paragraph*{Label Creation}
+
+As we chose a representation of labels as pairs of symbols (the
+label's name) and closures (the predicate corresponding to the label),
+label creation is relatively straightforward from the semantics:
+
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
+(define-syntax-rule (let-label l (lambda xs e) body)
+  (let ([l (labelpair (gensym 'lab)
+                      (lambda xs e))])
+    body))
 \end{lstlisting}
 
-As our definition is a transliteration of that in Figure 6 of Austin
-et. al's paper~\cite{Austin:2012}, we omit the implementation here.
-The result is a function, \code{mkfacet}, which (given a label and
-both positive and negative branches) forms a facet:
+\paragraph*{Faceted References}
 
-\begin{lstlisting}[language=Racket,escapechar=|,name=racets]
-(define (mkfacet label v1 v2)
-  (canonicalize (set-add (current-pc) (pos name)) v1 v2))
-\end{lstlisting}
+Our faceted semantics includes explicit \code{box} and \code{unbox}
+forms. This differs from Racket's semantics, where any variable may be
+treated as a box due to assignment conversion. We have two main
+options:
+
+\begin{itemize}
+\item Introduce an explicit \code{unbox} form in Racets, trusting the
+  programmer to explicitly use our implementation of \code{unbox} on
+  potentially-faceted objects.
+
+\item Walk over Racket code (after macro-expansion via
+  \code{local-expand}) transforming variable references to use
+  explicit \code{unbox} forms from Racets.
+\end{itemize}
+
+For our prototype of Racets, we have chosen to implement the
+first. This leads to a relatively simple implementation, but
+essentially trusts the programmer to use Racets' \code{unbox} forms
+when necessary.
+
+\begin{figure}
+(define-syntax (ref-set! stx)
+  (syntax-case stx ()
+    [(_ var e)
+     #`(let ([value e])
+         (let setf ([var var]
+                    [pc (current-pc)])
+           (if (box? var)
+               ; if var is a facet value
+               (set-box! var (construct-facet-optimized (set->list (current-pc)) value (unbox var)))
+               ; else
+               (mkfacet
+                (facet-labelname (unbox var))
+                (setf
+                 (facet-left (unbox var))
+                 (set-add pc (pos (facet-labelname var))))
+                (setf
+                 (facet-right (unbox var))
+                 (set-add pc (neg (facet-labelname var))))))))]))
+\caption{Racets' implementation of \code{set!}}
+\label{fig:setbang}
+\end{figure}
+
+Racets defines its \code{box} macro, along with \code{unbox} and
+\code{set!}. We include the definition of \code{set!} in
+Figure~\ref{fig:setbang}, which inlines the definition of the
+\textit{write} metafunction from Section~\ref{sec:semantics} to
+consider the case under which a facet is used when an address is
+expected.
 

### 2018-07-20 paper/paper.tex

@@
     \end{displaymath}
-              %%\inferrule[]
     \endgroup
     \label{fig:semantics}
+\end{figure*}
+
+\begin{figure*}
+  \hfill \textit{(Metafunctions)}
+      \\
+      \begin{displaymath}
+        \begin{array}{rclrr}
+          {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
+          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
+          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
+          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
+        \end{array}
+      \end{displaymath}
+      \\
+      \begin{displaymath}
+        \begin{array}{rclrr}
+          {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
+          {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
+          & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
+        \end{array}
+      \end{displaymath}
+      \\
+      \begin{displaymath}
+        \begin{array}{rclrr}
+          {obs(\ell, b, bv)} & {=} & {bv} & & \\
+          {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
+          {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
+          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = & \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
+        \end{array}
+      \end{displaymath}
 \end{figure*}

### 2018-07-21 paper/paper.tex
Pass over 4

@@
 \newcommand{\colorMATH}{black!20!blue}
+\newcommand{\colorCOMM}{0.133,0.545,0.133}
 \newcommand{\colorFAC}{black!20!red}
@@
 \begin{figure*}
-  \hfill \textit{(Metafunctions)}
-      \\
       \begin{displaymath}
@@
         \begin{array}{rclrr}
-          {write(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
-          {write(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = write(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
-          & & & \textit{and} ~ {\sigma'' = write(\sigma', v_2, pc \cup \{-\ell\}, v)}
+          {\var{write}(\sigma, \alpha, pc, v)} & {=} & {\sigma[\alpha ~ := \formfacet{pc}{v}{\sigma(\alpha)}]} & & \\
+          {\var{write}(\sigma, \facet{\ell}{v_1}{v_2}), pc, v} & = & {\sigma''} & \textit{where} ~ {\sigma' = \var{write}(\sigma, v_1, pc \cup \{+\ell\}, v)} \\
+          & & & \textit{and} ~ {\sigma'' = \var{write}(\sigma', v_2, pc \cup \{-\ell\}, v)}
         \end{array}
@@
       \end{displaymath}
+      \caption{Meta-functions used in our semantics}
+      \label{fig:metafunctions}
 \end{figure*}
@@
 \end{lstlisting}}
+}
 \caption{Facet creation as a macro}
@@
 
-\paragraph*{Faceted References}
+\paragraph*{Faceted Boxes, Writes, and Observations}
 
@@
 \begin{figure}
+\small
+\begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
 (define-syntax (ref-set! stx)
@@
     [(_ var e)
-     #`(let ([value e])
-         (let setf ([var var]
+     #`(let ([v e])
+         (let write ([var var]
                      [pc (current-pc)])
            (if (box? var)
-               ; if var is a facet value
-               (set-box! var (construct-facet-optimized (set->list (current-pc)) value (unbox var)))
-               ; else
+               ; <@$\color[rgb]{\colorCOMM}\var{write}(\sigma, \alpha, pc, v)$@>
+               (set-box! var (construct-facet (current-pc) v (unbox var)))
+               ; Else split
                (mkfacet
                  (facet-labelname (unbox var))
-                (setf
+                 ; <@$\color[rgb]{\colorCOMM}\var{write}(\sigma, \alpha, pc \cup \{+l\}, v)$@>
+                 (write
                    (facet-left (unbox var))
                    (set-add pc (pos (facet-labelname var))))
-                (setf
+                 ; <@$\color[rgb]{\colorCOMM}\var{write}(\sigma, \alpha, pc \cup \{-l\}, v)$@>
+                 (write
                    (facet-right (unbox var))
                    (set-add pc (neg (facet-labelname var))))))))]))
+\end{lstlisting}
 \caption{Racets' implementation of \code{set!}}
@@
 
-Racets defines its \code{box} macro, along with \code{unbox} and
+Racets defines a \code{box} macro, along with \code{unbox} and
 \code{set!}. We include the definition of \code{set!} in
@@
 
+Facet observation is handled similarly, first evaluating the label to
+produce a policy predicate, followed by evaluating the policy's
+argument and a possibly-faceted value to observe. After applying the
+policy its argument, we produce the value \bmth{v^{\pm}} and descend
+down the facet until reaching either a base value or finding the
+selected label (at which point we select the appropriate branch).
+
+\paragraph*{Faceted Function Application}
+
+By now we can anticipate a predictable pattern for implementing
+faceted execution: check \bmth{pc} to decide whether to branch left,
+right, or split. This is largely our strategy for handling faceted
+function application, with a small twist: we need to be able to apply
+functions from outside of Racets. For example, if we want to apply
+builtin functions such as \code{display}, we need to be mindful of the
+fact that these functions cannot work with faceted arguments.
+
+To handle this, we implement a macro for the \code{lambda} form, to
+tag Racet closures specifically (so that they are differentiated from
+functions outside of the current module). In the case that a foreign
+function is applied to a faceted value, our implementation of function
+application wraps the function to be able to handle facets by
+distributing the function through each branch of the facet.
+
+In general it is unsafe to apply an unknown function to a faceted
+value. This is because the unknown function may leak the facet's
+private information as a side-effect. Therefore, our current
+implementation of Racets allows programmers to apply external
+functions, but does not make any guarantee of safety. A better
+strategy may be to perform an \code{obs} before each call to a
+potentially-unsafe function. In general, we believe module
+interactions are a challenging problem in faceted execution, and we
+leave its study to future work.
+
+\section{Implementation and Evaluation}
+
+\section{Conclusion}
+
 \bibliographystyle{ACM-Reference-Format}
 \bibliography{paper}
-
 \end{document}

### 2018-07-22 paper/paper.tex
adding some text to sec 4

@@
 \newcommand{\bmth}[1] {{\color{\colorMATH} $#1$}}
+\newcommand{\rmth}[1] {{\color{\colorFAC} $#1$}}
 \newcommand{\code}[1]{\lstinline{#1}}
@@
 
-We now present a semantics for a core language (\lang) which includes
-facets. Our presentation largely mirrors that of Austin et
-al.~\cite{Austin:2013}. The syntax of our language---reminiscent of
-Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
-calculus with references (which have interact with facets in a subtle
-way) and three forms unique to faceted execution: facet construction, 
-label creation, and facet observation.
-
-\zw{Facet construction allows the users to construct a facet value that
-consists of a policy, a private/positive variable that can be a basic value
-or another facet value but is hidden away from other users, and a public/negative 
-variable. }
-
-\zw{Label creation dynamically creates a label binding to a given policy.
-A policy consists of a policy variable and a policy body/expression. 
-When a lable is invoked in the faceted executions, the policy will be called
-to evaluate the given faceted value. When the policy is invoked, the policy
-body (e.g. lambda function) evaluates to a boolean, which indicates whether
-to observe the positive or the negative branch of a faceted value. This allows
-the users to protect their data via choosing what data to be seen by others and 
-hiding the sensitive data.}
-
-\zw{Facet observation }
-
 \begin{figure*}
@@
     \endgroup
+    \caption{Semantics of Faceted Execution}
     \label{fig:semantics}
 \end{figure*}
+
+We now present a semantics for a core language (\lang) which includes
+facets. Our presentation largely mirrors that of Austin et
+al.~\cite{Austin:2013}. The syntax of our language---reminiscent of
+Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
+calculus with references (which have interact with facets in a subtle
+way) and three forms unique to faceted execution: facet construction, 
+label creation, and facet observation.
+
+Our semantics is shown in Figure~\ref{fig:semantics}. As faceted
+execution is an extension of the lambda calculus with references, we
+present the parts of the semantics unique to faceted execution in
+red. Base values in our semantics include addresses (used for boxes),
+constants, closures. We also include a special value \bmth{\star},
+which represents lazy failure: \bmth{\star} helps define the semantics
+of store update within a privileged context.
+
+Values in our semantics are either (unfaceted) base values or facets
+composed of a label and two branches. Facets can nest, allowing trees
+of faceted values. We define \emph{branches} as positive or negative
+labels. The program counter \rmth{pc} tracks the set of labels in the
+execution context. For example, to apply a faceted function to a value
+(for example \bmth{(\facet{\ell}{\lambda x.~0}{\lambda x.~1} 1)}), the
+semantics first applies the function along the positive branch
+extending the pc with \bmth{+\ell}, then applies the negative branch
+extending the pc with \bmth{-\ell}.
+
+The reduction relation \bmth{e, \rho, \sigma \Downarrow_{pc}^E \sigma,
+  v} reduces an expression, environment, and store to a resulting
+store and value. The first three rules (in all blue) are unchanged
+from the standard interpretation in the lambda calculus. The
+\textsc{Apply} rule calls out to the helper relation \rmth{(v~v),
+  \rho, \sigma \Downarrow_{pc}^A \sigma, v}, which applies a
+possibly-faceted value to an argument: if the value being applied is a
+plain (unfaceted) closure, the \textsc{App-Base} rule (in blue, as it
+is unchanged from the lambda calculus) applies it and returns
+immediately to the \bmth{\Downarrow_{pc}^E} relation.
+
+In the case that a faceted value is applied, \rmth{\Downarrow_{pc}^A}
+performs one of three functions, based on the relation of \rmth{\ell}
+to \rmth{pc}. If there is no occurrence of either \rmth{+\ell} or
+\rmth{-\ell} in \rmth{pc}, then the semantics must split the
+application. To do this, it applies both the positive and negative
+branches after extending \rmth{pc}. After reducing both branches to a
+value, the result is then formed into a facet. If \rmth{+\ell \in pc},
+then the semantics has already branched on the label \rmth{\ell}, so
+splitting would be redundant. In this case, \rmth{\Downarrow_{pc}^A}
+simply selects the positive branch to apply and continues without
+splitting. The symmetric case occurs in \textsc{App-Facet-Neg}. Facet
+formation follows this pattern, accounting for the relation of
+\rmth{\ell} to \rmth{pc}.
+
+The rule \text{Box}, \textsc{Unbox}, and \textsc{Set} are similar to
+the standard implementation of boxes, but with a slight twist: box
+creation, reads, and writes may occur within a privilaged context. To
+understand why, consider the following example\footnote{Our formal
+  semantics elides \code{if}, though it may be obtained via a Church
+  encoding if desired as in Austin et al.\cite{Austin:12}. Our
+  implementation includes \code{if} but not other constructs such as
+  \code{cond}}:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=boxexample]
+(define x (box 0))
+(if (= (facet alice 0 1) 0)
+  (set! x 0)
+  (set! x 1))
+(unbox x)
+\end{lstlisting}
+
+If we do nothing special to account for the fact that the program
+branches on the facet, control flow implicitly launders the value
+through the box to an unfaceted value. To fix this, we form a facet by
+taking into account \rmth{pc} and forming a facet using the
+meta-function \rmth{\formfacet{\ell}{v^+}{v^d}}. This meta-function is
+defined in Figure~\ref{fig:metafunctions}, and takes three arguments:
+the current \rmth{pc}, a positive view (\rmth{v^+}), and a ``default''
+view (\rmth{v^d}). Facet construction builds a facet with a spine
+corresponding to all of the labels in \rmth{pc}, and inserts
+\rmth{v^+} at the focus corresponding to \rmth{pc}, putting the
+default value \rmth{v^d} along all other branches. In the \code{box}
+form, the facet uses a default value of \bmth{\star}. In terms of our
+above example, this means that along the positive branch \code{x}
+would be set to \facet{\code{alice}}{1}{\star} (as the false branch of
+the \code{if} is taken), and along the subsequent negative branch
+\code{x} is extended to \facet{\code{alice}}{1}{0}.
 
@@
 \end{figure*}
+
+Label creation allocates a label as a fresh address in the store,
+binding the specified label predicate and adding it to the
+environment. Observation evaluates the label expression to an address
+and executes the associated predicate. Once this is done, \textsc{Obs}
+uses the \rmth{\var{obs}} meta-function to select the appropriate branch
+based on the value returned by the predicate associated with the
+label.
 

### 2018-07-23 paper/paper.tex
iterating on text in section 3

@@
 \newcommand{\colorMATH}{black!20!blue}
+\newcommand{\colorID}{black!20!blue}
 \newcommand{\colorCOMM}{0.133,0.545,0.133}
@@
 
-Our semantics is shown in Figure~\ref{fig:semantics}. As faceted
-execution is an extension of the lambda calculus with references, we
-present the parts of the semantics unique to faceted execution in
-red. Base values in our semantics include addresses (used for boxes),
-constants, closures. We also include a special value \bmth{\star},
-which represents lazy failure: \bmth{\star} helps define the semantics
-of store update within a privileged context.
+Our semantics is shown in Figure~\ref{fig:semantics}. As \lang is an
+extension of the lambda calculus with references, we present the parts
+unique to faceted execution in \fcol{red}, while keeping the lambda
+calculus with references in \blue{blue}. Base values in our semantics
+include addresses (used for boxes), constants, and closures. We also
+include a kind of lazy failure (\bmth{\star}), which is necessary for
+defining store update within a protected context.
 
@@
 composed of a label and two branches. Facets can nest, allowing trees
-of faceted values. We define \emph{branches} as positive or negative
-labels. The program counter \rmth{pc} tracks the set of labels in the
-execution context. For example, to apply a faceted function to a value
-(for example \bmth{(\facet{\ell}{\lambda x.~0}{\lambda x.~1} 1)}), the
-semantics first applies the function along the positive branch
-extending the pc with \bmth{+\ell}, then applies the negative branch
-extending the pc with \bmth{-\ell}.
+of faceted values. We use the term \emph{branches} to refer to
+positive or negated labels. Collections of branches define the program
+counter \rmth{pc}, which tracks the set of branches in the current
+context. For example, to apply a faceted function to a value (as in
+the application of \bmth{\facet{\ell}{\lambda x.~0}{\lambda x.~1}}),
+the semantics first applies \bmth{\lambda x.~0} while extending \rmth{pc}
+with \rmth{+\ell}, then applies the negative branch extending
+\rmth{pc} with \rmth{-\ell}.
 
@@
   v} reduces an expression, environment, and store to a resulting
-store and value. The first three rules (in all blue) are unchanged
+store and value. The first three rules (all in blue) are unchanged
 from the standard interpretation in the lambda calculus. The
@@
 to \rmth{pc}. If there is no occurrence of either \rmth{+\ell} or
-\rmth{-\ell} in \rmth{pc}, then the semantics must split the
-application. To do this, it applies both the positive and negative
-branches after extending \rmth{pc}. After reducing both branches to a
-value, the result is then formed into a facet. If \rmth{+\ell \in pc},
-then the semantics has already branched on the label \rmth{\ell}, so
-splitting would be redundant. In this case, \rmth{\Downarrow_{pc}^A}
-simply selects the positive branch to apply and continues without
-splitting. The symmetric case occurs in \textsc{App-Facet-Neg}. Facet
-formation follows this pattern, accounting for the relation of
-\rmth{\ell} to \rmth{pc}.
+\rmth{-\ell} in \rmth{pc}, then the semantics has not yet branched on
+\rmth{\ell}, and therefore must split the application. To do this, it
+applies both the positive and negative branches after extending
+\rmth{pc}. After reducing both branches to values, the results are
+formed into a facet. If \rmth{+\ell \in pc}, then the semantics has
+already branched on the label \rmth{\ell}, so splitting would be
+redundant. In this case, \rmth{\Downarrow_{pc}^A} simply selects the
+positive branch to apply and continues without splitting. The
+symmetric case occurs in \textsc{App-Facet-Neg}. Facet formation
+follows this pattern, accounting for the relation of \rmth{\ell} to
+\rmth{pc}.
 
-The rule \text{Box}, \textsc{Unbox}, and \textsc{Set} are similar to
-the standard implementation of boxes, but with a slight twist: box
-creation, reads, and writes may occur within a privilaged context. To
-understand why, consider the following example\footnote{Our formal
-  semantics elides \code{if}, though it may be obtained via a Church
-  encoding if desired as in Austin et al.\cite{Austin:12}. Our
-  implementation includes \code{if} but not other constructs such as
-  \code{cond}}:
+The rules \textsc{Box}, \textsc{Unbox}, and \textsc{Set} appear
+similar to the standard implementation of boxes, but employ several
+meta-functions to do their work. This is because box creation, reads,
+and writes may occur within a privilaged context, and care must be
+taken to form facets when \rmth{pc} is nonempty. To understand why,
+consider the following example\footnote{Our formal semantics elides
+  \code{if}, though it may be obtained via a Church encoding if
+  desired as in Austin et al.\cite{Austin:12}. Our implementation
+  includes \code{if} but not other constructs such as \code{cond}}:
 
@@
 binding the specified label predicate and adding it to the
-environment. Observation evaluates the label expression to an address
-and executes the associated predicate. Once this is done, \textsc{Obs}
-uses the \rmth{\var{obs}} meta-function to select the appropriate branch
-based on the value returned by the predicate associated with the
-label.
+environment. Labels must be store-allocated rather than bound in the
+lexical environment, as the latter would allow the label to be rebound
+by anyone using the facet:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=rebindingexample]
+(define alice-label (let-label l (lambda (x) (= x alice)) l))
+(define x (fac alice-label 1 0))
+(let ([alice-label (let-label l (lambda (x) #t) l)]) |\label{lineno:alicelab}|
+  (obs alice-label 1 x)) ; Should return |\facet{\texttt{alice-label}}{1}{0}|
+\end{lstlisting}
+
+The \code{obs} form in the above example ought to return
+\facet{\code{alice-label}}{1}{0}. But if we pull labels from the
+lexical environment, the binding on line~\ref{lineno:alicelab} shadows
+the policy originally associated with the facet.
+
+Last, observation evaluates the label expression to an address and
+executes the associated predicate. Once this is done, \textsc{Obs}
+uses the \rmth{\var{obs}} meta-function to select the appropriate
+branch based on the value returned by the predicate associated with
+the label. This meta-function accounts for the fact that the label
+being observed may appear arbitrarily deep in the facet (or not at
+all).
 

### 2018-07-23 paper/paper.tex
fixing title
merge complete

@@
 
-\title{Racets: Embedding Policy{-}Agnostic Programming in Racket}
+\title{Racets: Policy{-}Agnostic Programming in Racket}
 
@@
 branch, then again on the negative branch. Finally, the results of
-each branch are merged to produce a facet:
+each branch are merged to produce a facet.
 
@@
 
-Because the applied function could be stateful, faceted execution also
+Because the applied function can be stateful, faceted execution also
 records the current privilege level in a \emph{program counter}. The
@@
 Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
-calculus with references (which have interact with facets in a subtle
+calculus with references (which have interactions with facets in a subtle
 way) and three forms unique to faceted execution: facet construction, 
@@
 \begin{figure*}
+      %\begin{displaymath}
+      %  \begin{array}{rclrr}
+      %    {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
+      %    {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
+      %    {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
+      %    {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
+       % \end{array}
+      %\end{displaymath}
       \begin{displaymath}
         \begin{array}{rclrr}
-          {read(\sigma, \alpha, pc)} & {=} & {\sigma(\alpha)} & & \\
-          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_1, pc)} & \textit{if} ~ {+\ell} \in pc & \\
-          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {read(\sigma, v_2, pc)} & \textit{if} ~ {-\ell} \in pc & \\
-          {read(\sigma, \facet{\ell}{v_1}{v_2}), pc} & = & {\formfacet{\ell}{read(\sigma, v_1, pc)}{read(\sigma, v_2, pc)}} & \textit{otherwise} &
+          {\formfacet{\varnothing}{v_1}{v_2}} & {=} & {v_1} \\
+          {\formfacet{\{+\ell\} \cup rest}{v_1}{v_2}} & {=} & {\facet{\ell}{\formfacet{rest}{v_1}{v_2}}{v_2}} \\
+          {\formfacet{\{-\ell\} \cup rest}{v_1}{v_2}} & {=} & {\facet{\ell}{v_2}{\formfacet{rest}{v_1}{v_2}}}
         \end{array}
@@
       \end{displaymath}
-      \\
-      \begin{displaymath}
-        \begin{array}{rclrr}
-          {obs(\ell, b, bv)} & {=} & {bv} & & \\
-          {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
-          {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
-          {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = & \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
-        \end{array}
-      \end{displaymath}
+      %\\
+      %\begin{displaymath}
+      %  \begin{array}{rclrr}
+      %    {obs(\ell, b, bv)} & {=} & {bv} & & \\
+      %    {obs(\ell, true,} \facet{\ell}{v_1}{v_2}) & = & {v_1} & & \\
+      %    {obs(\ell, false,} \facet{\ell}{v_1}{v_2}) & = & {v_2} & & \\
+      %    {obs(\ell, b,} \facet{\ell'}{v_1}{v_2}) & = & \facet{\ell'}{obs(\ell,b,v_1)}{obs(\ell,b,v_2)} & \textit{where} & {\ell} \neq {\ell'}
+      %  \end{array}
+      %\end{displaymath}
       \caption{Meta-functions used in our semantics}
@@
 whether or not to reveal a facet's positive or negative
-branch. However, there is a subtle issue: facet canonicalization
-relies upon a total order for labels. In light of this, we represent
-labels as a pair of a name and a policy:
+branch. Therefore, we represent labels as a pair of a name and a policy:
 
@@
               {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
-                \boxed{\{+\ell, -\ell\} \cup pc = \varnothing} \\\\
+                \boxed{\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
                 e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
@@
 
-At first glance, it may not be obvious that we even \emph{need} a maco
+At first glance, it may not be obvious that we even \emph{need} a macro
 for facet creation. But according to our semantics, the following

### 2018-07-23 paper/paper.tex
some comments on sec 3 and 4

@@
         \begin{array}{rclrr}
-          {\formfacet{\varnothing}{v_1}{v_2}} & {=} & {v_1} \\
-          {\formfacet{\{+\ell\} \cup rest}{v_1}{v_2}} & {=} & {\facet{\ell}{\formfacet{rest}{v_1}{v_2}}{v_2}} \\
-          {\formfacet{\{-\ell\} \cup rest}{v_1}{v_2}} & {=} & {\facet{\ell}{v_2}{\formfacet{rest}{v_1}{v_2}}}
+          {\formfacet{\varnothing}{v^+}{v^d}} & {=} & {v^+} \\
+          {\formfacet{\{+\ell\} \cup rest}{v^+}{v^d}} & {=} & {\facet{\ell}{\formfacet{rest}{v^+}{v^d}}{v^d}} \\
+          {\formfacet{\{-\ell\} \cup rest}{v^+}{v^d}} & {=} & {\facet{\ell}{v^d}{\formfacet{rest}{v^+}{v^d}}}
         \end{array}
@@
 being observed may appear arbitrarily deep in the facet (or not at
-all).
+all). \zw{We elide the description of the meta-function \rmth{\var{obs}}
+here, but it is fully described in Austin et al.~\cite{Austin:2012}}
 
@@
 consider the case under which a facet is used when an address is
-expected.
+expected. \zw{The role of the \textit{write} metafunction is to 
+recursively dig into faceted value, and make writes to the addresses.
+If it is an address at the beginning, which hits the base case,
+the \textit{write} metafunction constructs a new faceted value according
+to \bmth{pc} and makes modification to the address.}
 

### 2018-07-23 paper/paper.tex
recent work on 1

@@
 directly into application code. Instead, data is labeled with its
-policy as it enters the system, and propagates through the program as
-computation progresses. Policy-agnostic programming is often
-implemented using faceted execution, a dynamic information-flow
-monitor encoding sensitive values as \emph{facets}: decision trees
-specifying different views of that data. For example, the facet
-\facet{Alice}{\code{#t}}{\code{#f}} represents a value that should
-appear to Alice as \code{#t} and to everyone but Alice as \blue{\code{#f}}.
+policy as it enters the system, and policies propagate through the
+program alongside data as computation progresses. Policy-agnostic
+programming is often implemented using \emph{faceted execution}, a
+dynamic information-flow monitor encoding sensitive values as
+\emph{facets}: decision trees specifying different views of that
+data. For example, the facet \facet{Alice}{\code{true}}{\code{false}}
+represents a value that should appear to Alice as \blue{\code{true}} and to
+everyone but Alice as \blue{\code{false}}.
 
 Faceted execution propagates facets by extending core linguistic
-primitives (such as function application). For example, consider the
-application \code{(not x)} where \code{x} is
-\blue{\facet{Alice}{\code{#t}}{\code{#f}}}. The programmer intends the
-call to \code{not} to be operating on a \code{boolean?}, but because
-\code{x} is a facet this call produces \code{#f} instead. The correct
-way to interpret function application on facets is to distribute the
-application through each branch, producing \zw{producing ...?} %% \code{m
-  %% \mc{ \facet{Alice}{\code{#f}}{\code{not #t}}}}
-. Other core forms
-(such as \code{if}, \code{cond}, etc...) require similar changes.
+primitives (such as function application) to handle faceted
+values. For example, consider the application \blue{\code{(x true)}} where
+\code{x} is \blue{\facet{Alice}{\lambda x.~\code{true}}{\code{not}}}.
+Racket's standard function application will fail here because Racket's
+\blue{\code{ppapp}} expects a procedure rather than a facet.  The correct way
+to interpret function application on facets is to distribute the
+application through each branch, producing
+\facet{Alice}{\code{true}}{\code{false}}. Many other core forms (such
+as \code{if}, \code{set!}, etc...) require similar changes.
 
-The core linguistic changes required by faceted execution have led to
-relatively inelegant and heavyweight implementations thusfar. For
-example, Flanagan et. al (who first presented faceted execution)
-extended the JavaScript runtime to account for faceted
-values. Similarly, the Jeeves programming language does (what does it
-do?)\zw{Need to complete this sentence}. By contrast, Racket's 
-highly-expressive macro system allows even
-core forms (such as \code{#\%app}) to be redefined with relative ease.
+Policy-agnostic programming promotes the idea that programmers should
+be able to write programs ``normally'', without concerning themselves
+with how privacy policies are enforced. And yet, we believe that the
+relatively foundational linguistic changes required to enable faceted
+execution have hindered implementations thusfar. For example, the
+first implementation of faceted execution (by Austin et
+al.~\cite{Austin:12}) extended a JavaScript interpreter to account for
+faceted values. Other implementations use monads~\cite{Schmitz:2016}
+or rely upon third-party macro systems~\cite{Yang:2016}. So far, we
+know of no implementation of faceted execution that works seamlessly
+alongside the language. By contrast, Racket has a powerful macro
+system, allowing essentially any linguistic form (including function
+application) to be extended with arbitrary semantics.
 
@@
   (if (null? board)
-      (cons board #f)
+      (cons board false)
       (let* ([fst (car board)]
@@
                  (= (cdr fst) y))
-            (cons rst #t)
+            (cons rst true)
             (let ([rst+b (mark-hit rst x y)])
@@
   \begin{array}{lcrcl}
-    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{\#t} \mid \code{\#f} \mid \ldots} \\
+    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{true} \mid \code{false} \mid \ldots} \\
     \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \blue{\ldots}  \\
@@
 (define x (fac alice-label 1 0))
-(let ([alice-label (let-label l (lambda (x) #t) l)]) |\label{lineno:alicelab}|
+(let ([alice-label (let-label l (lambda (x) true) l)]) |\label{lineno:alicelab}|
   (obs alice-label 1 x)) ; Should return |\facet{\texttt{alice-label}}{1}{0}|
@@
 for facet creation. But according to our semantics, the following
-snippet should produce \code{#t} if \bmth{+\ell \in pc}:
+snippet should produce \code{true} if \bmth{+\ell \in pc}:
 
 \begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=other,numbers=none]
-(fac l #t (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
+(fac l true (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
 \end{lstlisting}

### 2018-07-23 paper/paper.tex
Committing some bug fixes for various macros

@@
             \{+\ell, -\ell\} \cap pc = \varnothing \\\\
-           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
-           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
-           v = \formfacet{pc}{v_1}{v_2}}
+           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \and
+           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \\\\
+           v = \formfacet{pc \cup \{+\ell\}}{v_1}{v_2}}
           {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
@@
           \inferrule[\textsc{Fac-Create-Pos}]
-          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \\\\
            + \ell \in pc \\\\
@@
           \inferrule[\textsc{Fac-Create-Neg}]
-          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \and
+          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \\\\
            - \ell \in pc \\\\
@@
 
+\kris{TODO: FIX THIS (make consistent w semantics)}
 \[\small
@@
                       ([current-pc (set-add (current-pc)
-                                            (neg (facet-labelname l)))]))]
-           (mkfacet (labelpair-name l) v1 v2)))]))
+                                            (neg (facet-labelname l)))]))])
+           (mkfacet (set-union (set (pos (labelpair-name l)))
+                                    (current-pc))
+                    v1 v2))]))
 \end{lstlisting}}

### 2018-07-23 paper/paper.tex
various tweaks to bib and adding a tiny bit of impl sec

@@
 
+We have implemented Racets as a set of Racket macros which can be
+employed as a language using Racket's \texttt{\#lang reader}
+facility. So far, we have included macros for many of Racket's core
+forms including application, \code{if}, \code{lambda}, and
+references. We leave others (including continuation marks) to future
+work. Additionally, Racets does not support first-class control. There
+has been recent work in handling exceptions in the context of faceted
+execution~\cite{Austin:17}, however reconciling first-class control in
+general remains (to our knowledge) an open problem.
+
+Because of Racket's flexible macro system, our implementation of
+faceted execution is much smaller than other systems: our core macros
+comprise only 170 source lines of Racket, with another 120 lines of
+library code to perform various facet-related functions.
+
+We plan to make our prototype of Racets available publicly.
+
 \section{Conclusion}

### 2018-07-23 paper/paper.tex
edits to intro

@@
 \newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
+\newcommand{\racets}[0]{$\textsc{Racets}$\xspace}
 \newcommand{\facet}[3]{{\fcol{\ensuremath{\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}}}}
@@
 
-\title{Racets: Policy{-}Agnostic Programming in Racket}
+\title{\racets: Policy{-}Agnostic Programming in Racket}
 
@@
 \affiliation{%
- \institution{University of Alabama}
+ \institution{University of Alabama, Birmingham}
  \city{Birmingham}
@@
 
-\keywords{security, faceted execution, information flow, macros}
+\keywords{security, faceted execution, macros, information flow, languages as libraries}
 
@@
 
-As our systems become more interconnected, they consume an
-ever-growing amount of data.  System designers communicate to users
-how their data is used via a \emph{privacy policy}. Unfortunately,
-implementing these policies correctly is challenging: users often have
+As information systems become more interconnected and complex, they consume an
+ever-growing amount of private data. System designers communicate to users
+how their data may be used via a \emph{privacy policy}. Unfortunately,
+implementing such policies correctly is challenging: users often have
 partial control over the policy (e.g., whether their phone number is
-publicly visible or private) and policies change frequently (e.g.,
-after new laws are passed). As policies evolve, developers face
-massive (re)engineering efforts to ensure that implementations match
-the espoused policy.
+publicly visible or private) and policies can change frequently.
+Not only can specific privacy policies be highly dynamic (dependent on runtime values),
+but the process of improving privacy policies can be highly dynamic across time.
+As policies evolve, developers face massive (re)engineering efforts to
+ensure that implementations continue to match the policy at every relevant
+point in the codebase.
 
@@
 decouples the implementation of privacy policies from the code that
-operates on sensitive data. This frees developers to write programs as
-they would normally, without inserting logic to manage the policy
-directly into application code. Instead, data is labeled with its
-policy as it enters the system, and policies propagate through the
-program alongside data as computation progresses. Policy-agnostic
-programming is often implemented using \emph{faceted execution}, a
-dynamic information-flow monitor encoding sensitive values as
-\emph{facets}: decision trees specifying different views of that
-data. For example, the facet \facet{Alice}{\code{true}}{\code{false}}
+operates on sensitive data. This frees developers to write programs mostly
+as they would for insecure code, without inserting specific logic to manage
+information-flow policies directly into application code. Instead, data is
+labeled with its policy as it enters the system and such labels propagate through
+the program, alongside data, as computation progresses. When a secure value needs
+to be introspected upon (or propagates outside the application), its policy
+can be invoked at this point dynamically. This paradigm aims to permit
+code manipulating sensitive data to be written in a manner entirely orthogonal to
+policies themselves.
+
+\emph{Faceted execution} (FE) is a highly expressive (but potentially expensive)
+language semantics enabling policy-agnostic programming. In FE, dynamic information-flow
+monitors instrument the program, encoding sensitive values as \emph{faceted values}:
+decision trees specifying different views of data according to different possible security labels.
+For example, the faceted value \facet{Alice}{\code{true}}{\code{false}}
 represents a value that should appear to Alice as \blue{\code{true}} and to
-everyone but Alice as \blue{\code{false}}.
-
-Faceted execution propagates facets by extending core linguistic
-primitives (such as function application) to handle faceted
-values. For example, consider the application \blue{\code{(x true)}} where
+everyone except Alice as \blue{\code{false}}. Faceted execution propagates distinct facets
+of a value by extending core linguistic primitives (such as function application).
+For example, consider the application \blue{\code{(x true)}} where
 \code{x} is \blue{\facet{Alice}{\lambda x.~\code{true}}{\code{not}}}.
 Racket's standard function application will fail here because Racket's
-\blue{\code{ppapp}} expects a procedure rather than a facet.  The correct way
-to interpret function application on facets is to distribute the
-application through each branch, producing
-\facet{Alice}{\code{true}}{\code{false}}. Many other core forms (such
-as \code{if}, \code{set!}, etc...) require similar changes.
+\blue{\code{ppapp}} expects a procedure rather than a facet. Instead, the proper way
+to interpret function application on faceted values is to distribute the
+application over all (in this case, both) facets, producing
+\facet{Alice}{\code{true}}{\code{false}}: if Alice is viewing, the application yielded true,
+otherwise it yielded false, so both are computed until the value is explicitly observed
+with specified permissions. Many other core forms (such
+as \code{if}, \code{set!}, etc...) require similar changes to handle faceted
+values correctly.
 
@@
 be able to write programs ``normally'', without concerning themselves
-with how privacy policies are enforced. And yet, we believe that the
+with how privacy policies are enforced. Unfortunately, the
 relatively foundational linguistic changes required to enable faceted
-execution have hindered implementations thusfar. For example, the
-first implementation of faceted execution (by Austin et
-al.~\cite{Austin:12}) extended a JavaScript interpreter to account for
-faceted values. Other implementations use monads~\cite{Schmitz:2016}
-or rely upon third-party macro systems~\cite{Yang:2016}. So far, we
-know of no implementation of faceted execution that works seamlessly
-alongside the language. By contrast, Racket has a powerful macro
-system, allowing essentially any linguistic form (including function
-application) to be extended with arbitrary semantics.
+execution have hindered implementations thusfar. Dynamic generation
+of first-class security labels, tracking an arbitrary number of
+facets per value, and keeping facted-value trees in a canonical order,
+are all central challenges in any practical implementation. For example, the
+first implementation of FE (by \citet{Austin:2012}) extended
+a JavaScript interpreter to account for faceted values. Other
+implementations use monads~\cite{Schmitz:2016}
+or rely upon third-party macro systems~\cite{Yang:2016}. We
+know of no existing implementation of FE that aims to interoperate seamlessly
+with code written in the host language. By contrast, Scheme boasts a powerful
+hygenic macro system that allows essentially any linguistic form
+to be modified arbitrarily.
 
-In this paper we present Racets, an implementation of policy-agnostic
-programming in Racket via macros. Racets provides facilities for
-creating policies and faceting secure data with those policies. Racets
+In this paper we present \racets, an implementation of policy-agnostic
+programming in Racket via macros. \racets provides facilities for
+creating policies and faceting secure data with those policies. \racets
 also extends several core forms in Racket to work with faceted
 values (our implementation is detailed in Section~\ref{sec:implementation}). We
-have measured the overhead of Racets in several microbenchmarks, and
-have used Racets to implement a small server-based
-board-game (detailed in Section~\ref{sec:evaluation}). We see Racets as a
+have measured the overhead of \racets in several microbenchmarks, and
+have used \racets to implement a small server-based
+board-game (detailed in Section~\ref{sec:overview}). We see \racets as a
 promising prototype for policy-agnostic programming in Racket, and
-conclude with several future directions in Section~\ref{sec:conclusion}.
+conclude with discussion of future directions in Section~\ref{sec:conclusion}.
 
 \section{Overview of Faceted Execution}
+\label{sec:overview}
 
 To introduce our setting we present the implementation of Battleship,
-a small guessing-based board game, in Racets (this section presents a
+a small guessing-based board game, in \racets (this section presents a
 distilled version of our case study in
@@
 \section{Faceted Execution as Macros}
+\label{sec:implementation}
 
@@
 straightforward. This section of our paper describes the design of
-Racets, a prototype implementation of faceted execution using Racket
+\racets, a prototype implementation of faceted execution using Racket
 macros. In Section~\ref{sec:conclusion} we remark upon current
-directions scaling Racets to the whole of Racket.
+directions scaling \racets to the whole of Racket.
 
@@
 mechanisms (such as continuation marks\kris{cite}, to which parameters
-macro-expand) could also be used. Racets defines the parameter
+macro-expand) could also be used. \racets defines the parameter
 \code{current-pc}, and updates it as computation progresses:
@@
 \begin{itemize}
-\item Introduce an explicit \code{unbox} form in Racets, trusting the
+\item Introduce an explicit \code{unbox} form in \racets, trusting the
   programmer to explicitly use our implementation of \code{unbox} on
@@
   \code{local-expand}) transforming variable references to use
-  explicit \code{unbox} forms from Racets.
+  explicit \code{unbox} forms from \racets.
 \end{itemize}
 
-For our prototype of Racets, we have chosen to implement the
+For our prototype of \racets, we have chosen to implement the
 first. This leads to a relatively simple implementation, but
-essentially trusts the programmer to use Racets' \code{unbox} forms
+essentially trusts the programmer to use \racets' \code{unbox} forms
 when necessary.
@@
 \end{lstlisting}
-\caption{Racets' implementation of \code{set!}}
+\caption{\racets' implementation of \code{set!}}
 \label{fig:setbang}
@@
 
-Racets defines a \code{box} macro, along with \code{unbox} and
+\racets defines a \code{box} macro, along with \code{unbox} and
 \code{set!}. We include the definition of \code{set!} in
@@
 function application, with a small twist: we need to be able to apply
-functions from outside of Racets. For example, if we want to apply
+functions from outside of \racets. For example, if we want to apply
 builtin functions such as \code{display}, we need to be mindful of the
@@
 private information as a side-effect. Therefore, our current
-implementation of Racets allows programmers to apply external
+implementation of \racets allows programmers to apply external
 functions, but does not make any guarantee of safety. A better
@@
 
-We have implemented Racets as a set of Racket macros which can be
+We have implemented \racets as a set of Racket macros which can be
 employed as a language using Racket's \texttt{\#lang reader}
@@
 references. We leave others (including continuation marks) to future
-work. Additionally, Racets does not support first-class control. There
+work. Additionally, \racets does not support first-class control. There
 has been recent work in handling exceptions in the context of faceted
@@
 
-We plan to make our prototype of Racets available publicly.
+We plan to make our prototype of \racets available publicly.
 
 \section{Conclusion}
+\label{sec:conclusion}
+
+asdf asdf
 

### 2018-07-23 paper/paper.tex
small tweaks

--- 2018-07-23 paper/paper.tex
@@
   (define alice-board
-          (facet alice-label (add-pieces (makeboard) x|$_1$| y|$_1$| |$...$|) star))
+          (facet alice-label (add-pieces (makeboard) x|$_1$| y|$_1$| |$...$|) (|\bmth{\star}|)))
 \end{lstlisting}
@@
     & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
-    & & & \blue{\mid} & \blue{(\code{let-label} ~ \ell ~ e ~ e)} \\
-    & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\
-    & & & \blue{\mid} & \blue{(\code{obs} ~ e ~ e ~ e)} \\
+    & & & \fcol{\mid} & \fcol{(\code{let-label} ~ \ell ~ e ~ e)} \\
+    & & & \fcol{\mid} & \fcol{(\code{facet} ~ e ~ e ~ e)} \\
+    & & & \fcol{\mid} & \fcol{(\code{obs} ~ e ~ e ~ e)} \\
   \end{array}
@@
 \label{fig:syntax}
-\caption{Syntax of \lang}
+\caption{Syntax of \lang. Forms unique to facets are shown in \fcol{red}.}
 \end{figure}

### 2018-07-23 paper/paper.tex
pass on section 2

--- 2018-07-23 paper/paper.tex
@@
 have used \racets to implement a small server-based
-board-game (detailed in Section~\ref{sec:overview}). We see \racets as a
+board-game (detailed in Sections~\ref{sec:overview} and~\ref{sec:implementation}). We see \racets as a
 promising prototype for policy-agnostic programming in Racket, and
@@
 
-To introduce our setting we present the implementation of Battleship,
-a small guessing-based board game, in \racets (this section presents a
+To introduce faceted execution more concretely, we present the implementation
+of Battleship, a small guessing game, in \racets (this section presents a
 distilled version of our case study in
-Section~\ref{sec:case-study}). In this game each player has a
-grid-based board on which they place tiles (or ``ships''). The players
+Section~\ref{sec:implementation}). In this game each player has a
+private board of coordinates, at which they place ``ships''. The players
 hide their boards from each other as play progresses in rounds. Each
-turn a player guesses the position of a tile on the other player's
-board. If the guess is successful that tile is removed from the
-board. Play ends once one player's board has no remaining tiles, at
-which point that player loses.
+turn a player guesses the position of a ship on the other player's
+board. If the guess is successful the tile is removed from the
+board and a hit is declared publically. Play ends once one player's board
+has no remaining tiles, at which point that player loses.
 
 We implement game boards as lists of cons cells representing the
-\blue{$(x,y)$} coordinates of ships. Board creation is simply the empty
+\blue{$(x,y)$} coordinates of ships. Board creation simply returns an empty
 list, and adding a piece is done via \lstinline|cons|:
@@
 When Alice and Bob want to play a game, they both create a
-\emph{label} to protect their data. A label is a predicate that takes
-an argument and, if it returns true, reveals a secret. Alice's label
-is used to annotate whatever data she wants to be kept
-secret. Supposing Alice chooses to be player 1, she will use the
+\emph{label} to protect their data. A label is unique id mapped to a policy predicate
+that takes an key (e.g., the current user's name) and returns true or false to indicate
+permission for the label. Alice's label is used to annotate data she wants
+to be kept secret. Supposing Alice chooses to be player 1, she may use the
 following label:
@@
 
-Bob would use a similar label (but with 2 instead of 1). At runtime,
-the \code{label} form creates a label \blue{$\ell_{A}$} and returns it
-to the binding for \code{alice-label}. When Alice wants to protect a
+This code illustrates label creation, policy predicates, and the first-class
+nature of labels. The policy predicate $\texttt{($\lambda$ (\blue{x}) (= 1 \blue{x}))}$
+grants permission to player 1 only and is associated with the dynamically generated
+label l (returned and bound to \texttt{\blue{alice-label}}).
+Bob would use a similar policy (but for player $2$ instead of $1$). At runtime,
+the \code{let-label} form creates a label \blue{$\ell_{A}$} and binds
+it to a closure for its policy predicate. When Alice wants to protect a
 value, she creates a facet annotated with her label and two
@@
 
-In the above example, Alice uses \blue{$\star$} (lazy failure) to
-represent that others should see nothing if they observe the data. In
-other applications, she might choose a more sensible default value to
-reveal to others. She may even want to create a \emph{nested}
-facet. For example, in a social-networking application she may want a
+In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
+to ensure execution will fail if Bob tries to observe Alice's secret gameboard.
+The $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ \blue{e_\text{fac}}\code{)}$ form takes
+a label, a key, and a facted value. Explicit observation projects a single label
+$\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ to either its positive or negative facet,
+depending on whether the policy associated with $\blue{e_\ell}$ returns true for key
+$\blue{e_\text{key}}$. If Bob tries to observe Alice's board, the policy predicate
+will return false (from \texttt{(= 1 $\blue{2}$)}) and Alice's negative facet $\blue{\star}$ will result.
+
+In other applications, Alice might choose a sensible default value to
+reveal to others---she may even want to create a \emph{nested}
+facet. For example, a social-networking application might use a
 nested facet consisting of two labels for
-\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. She
-would present three views of her social-media profile: \bmth{p_1} to
+\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
+could then present three views of her social-media profile: \bmth{p_1} to
 her family, containing her phone number and other contact information,
@@
 
-As play of the game progresses, Alice and Bob both make guesses, and a
-driver calls the function \code{mark-hit} with each of their (faceted)
-game boards. However, because Alice and Bob's game boards are both
-facets, \code{mark-hit} cannot be immediately applied, as the argument
-\code{board} is a facet. Faceted execution ``splits'' the execution of
-the function on faceted arguments, running it first on the positive
+As a game of Battleship progresses, Alice and Bob make guesses in turn, and
+driver code calls the function \code{mark-hit} with each of their respective
+(faceted) game boards to record the attack. However, because Alice and Bob's
+game boards are both faceted values, \code{mark-hit} cannot be directly applied as
+in normal execution. Instead, faceted execution ``splits'' the evaluation of
+the function application over both facets, running it first on the positive
 branch, then again on the negative branch. Finally, the results of
-each branch are merged to produce a facet.
+each branch are combined again to produce a new faceted value. This allows FE
+to avoid needing to reason about labels and policies until an explicit observation
+point where a policy is checked and a faceted value is projected to one of its
+facets.
 
@@
 Because the applied function can be stateful, faceted execution also
-records the current privilege level in a \emph{program counter}. The
-program counter is used to build facets when writes are made to the
-store inside of a privileged context. We expand upon these subtleties
-in Section~\ref{sec:semantics}, where we present a full semantics for
-faceted execution.
-
-\kris{Stuff about obs here..}
+maintains the current privilege level in a \emph{program counter} (PC). The
+program counter is a property of the current evaluation context and is used
+to build facets when writes are made to the store in a privileged context.
+For example, if a stateful function ``splits'' when applied on both the positive and negative
+facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
+the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
+FE semantics will set $x$ to $\facet{\ell}{3}{2}$ so that the value $3$
+cannot be leaked from the secure context (speculative execution under the
+$\blue{+\ell}$ facet). This is because, for the duration of the the app ``split'',
+the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
+and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
+not make this faceting explicit, a senstive value could leak from one PC to another.
+We expand upon these subtleties in Section~\ref{sec:semantics},
+where we present a complete semantics for faceted execution.
 
@@
   \begin{array}{lcrcl}
-    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{true} \mid \code{false} \mid \ldots} \\
-    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \blue{\ldots}  \\
+    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{'() \mid \code{true} \mid \code{false} \mid \ldots} \\
+    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \langle\textit{program variables}\rangle  \\
     \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
@@
     & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
-    & & & \blue{\mid} & \blue{(\code{let-label} ~ \ell ~ e ~ e)} \\
+    & & & \blue{\mid} & \blue{(\code{let-label} ~ x ~ e ~ e)} \\
     & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\

### 2018-07-24 paper/paper.tex
pass over 4

@@
 \usepackage{xcolor}
+\usepackage[labelsep=quad,indention=10pt]{subfig}
 \usepackage{mathpartir} % Inference rules
@@
 faceted execution is much smaller than other systems: our core macros
-comprise only 170 source lines of Racket, with another 120 lines of
+comprise roughly 170 source lines of Racket, with another 120 lines of
 library code to perform various facet-related functions.
 
-We plan to make our prototype of \racets available publicly.
+\paragraph*{Case Study: Battleship in Racets}
+
+\begin{figure*}
+  \subfloat[]{%
+    \includegraphics[height=1.1in]{a.png}%
+    \label{fig:player1}%
+  } 
+  \quad
+  \subfloat[]{%
+    \includegraphics[height=1.1in]{b.png}%
+    \label{fig:player1player2}%
+  }
+  \quad
+  \subfloat[]{%
+    \includegraphics[height=.7in]{c.png}%
+    \label{fig:player2strike}%
+  }
+  \vspace{.3in}
+  \quad
+  \subfloat[]{%
+    \includegraphics[height=1.1in]{d.png}%
+    \label{fig:player1afterstrike}%
+  }
+  \caption{Screenshots from our Battleship case study.}
+  \label{fig:case}
+\end{figure*}
+
+To gain perspective on how Racets enables policy-agnostic programming,
+we scaled our implementation from Section~\ref{sec:overview} to a
+web-based game of Battleship written in Racets. Our implementation
+uses Racket's \texttt{web-server} framework~\cite{webserver}, which
+defines an API for writing HTTP-based server applications.
+
+Figure~\ref{fig:case} shows several screenshots of our Battleship
+application. The first screenshot~\ref{fig:player1} shows the board as
+viewed by player 1 (note the parameter \texttt{/player1/player1}),
+while the second shows the empty board observed when player 2 attempts
+to view player 1's board. The screenshot in~\ref{fig:player2strike}
+shows the response seen by player 2 upon a successful hit. Finally
+screenshot~\ref{fig:player1afterstrike} shows player one's board with
+the ship on \bmth{(3,2)} removed.
+
+When running, our game server provides several routes that a user can
+access:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=case]
+(define-values (dispatch generate-url)
+  (dispatch-rules
+    [("player1" (string-arg)) player1board]
+    [("player2" (string-arg)) player2board]
+    [("player1strike" (string-arg)) p1strike]
+    [("player2strike" (string-arg)) p2strike]))
+\end{lstlisting}
+
+The route \texttt{/player1/<id>} (or \texttt{/player2/<id>}) renders
+player 1's game board when viewed as \texttt{<id>}. We facet game
+boards with policies that reveal player 1's board when \texttt{<id>}
+is \texttt{player1}, and do the same with player 2:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=case]
+(define p1l (mkpol "player1"))
+(define p1board
+  (box (fac p1l
+            (add-pieces (makeboard) '(1 2 ldots))
+            (makeboard))))
+\end{lstlisting}
+
+The board is explicitly made into a box: this is because the board's
+state will change as player 2 makes moves and eliminates pieces from
+their board. The \code{player1board} function implements the logic to
+render player 1's board as an HTML table. The argument \code{viewer}
+corresponds to the \texttt{<id>} route argument, and is passed to
+\code{player1board} by the framework. This argument is then used to
+observe the board game
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=case]
+(define player1board
+  (ext-lambda (request viewer)
+         (http-response "<h1>Player 1's Game Board</h1>"
+                        (pretty-print 
+                           (obs p1l name (deref p1board))))))
+\end{lstlisting}
+
+The implementation of \code{player1board} uses a special form
+\code{ext-lambda}, discussed at the end of this section, to allow code
+from Racets to be executed by the framework (which is not prepared to
+execute faceted code).
+
+The function \code{p1strike} allows player 1 to make a guess as to the
+position of ships on player 2's board. The function parses the
+position into two coordinates and then calls \code{mark-hit} to
+perform the hit, updating player 2's board and then observing the
+result to answer (to player 1) whether the result was a hit or not:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=case]
+(define p1strike
+  (ext-lambda
+   (request position)
+   (let* ([x (char-to-num (string-ref position 0))]
+          [y (char-to-num (string-ref position 2))]
+          [ans (mark-hit p2board x y)]
+      (set! p2board (car ans))
+      (http-response
+       (if (cdr (obs p2l "player2" ans)) |label{lineno:explicitobs}|
+           "<h1>Congratulations!</h1> <h4>You hit player 2!</h4>"
+           "<p>No hit :(</p>")))))))
+\end{lstlisting}
+
+Note that we need to use an explicit \code{obs} form on
+line~\ref{lineno:explicitobs}. This is because---as \code{p2board} is
+a facet---the result will also be a faceted value. When we want to
+display the output to player 1, our code needs to explicitly observe
+the answer, as \code{http-response} cannot accept a faceted value.
+
+\paragraph*{}
 

### 2018-07-24 paper/paper.tex
small tweaks
nit

@@
 To handle this, we implement a macro for the \code{lambda} form, to
-tag Racet closures specifically (so that they are differentiated from
+tag \racets closures specifically (so that they are differentiated from
 functions outside of the current module). In the case that a foreign
@@
 library code to perform various facet-related functions.
+
+Our implementation is currently available on Github at
+\blue{\url{https://github.com/fordsec/racets}}
 

### 2018-07-24 paper/paper.tex
adding related work

@@
 
+\section{Related Work and Future Directions}
+
+To the best of our knowledge, we are the first authors to present an
+implementation of faceted execution using hygienic macros. There are
+several threads of related work in dynamic information flow and
+programming paradigms for information flow.
+
+Information-flow was first formalized by \citet{Denning:1976}.
+In her seminal work on a lattice model
+for information flow, she outlined challenges and potential solutions
+to static information-flow checking. Subsequently, \citet{Goguen:82}
+defined noninterference, which formalized the idea that privileged
+data should not influence publicly observable
+outputs. \citet{Clarkson:08} later recognized that
+information-flow properties fit into a class of program properties
+that could not be characterized by a single trace of a program, but
+rather a set of traces, and called these hyperproperties.
+
+Along with definitions of information flow, there has also been
+significant interest in mechanisms for enforcing information
+flow. This work can be broadly divided into static and dynamic
+enforcement mechanisms for information flow security. Of the
+mechanisms for static information flow, security type systems have
+gained the most use. First introduced by \citet{Volpano:1997}, these
+type systems augment the binding environment to track the privilege of
+variables and prevent writes to variables that would violate
+noninterference. Myers leveraged this idea to produce Jif, a variant
+of Java with an information-flow type
+system~\cite{Myers:1999}. Security type systems have been subsequently
+extended to accommodate concurrent programs~\cite{Zdancewic:03} and
+flow sensitivity~\cite{Hunt:2006}. Faceted execution does not require
+annotating the program with security types, but at the expense of
+losing a static characterization of the program's security in its type
+system.
+
+\citet{Devriese:10} first introduced secure multi-execution as a
+dynamic enforcement technique for information flow. Secure
+multi-execution runs $2^k$ copies of a program in parallel, where each
+run represents a subset of $\wp(\var{Prin})$, where $\var{Prin}$ is a
+set of principals. For example, if the principals in the program are
+Alice and Bob, secure multi-execution executes four copies of the
+program: one that replaces all secret inputs by $\bot$, one that
+replaces Bob's input by $\bot$ but Alice's input by the true input,
+one for Bob's input, and one with access to all privilaged
+information. When external effects are made (e.g., writing to disc),
+the runtime can select which variant to use based on a policy. Secure
+multi-execution prevents information flow violations at runtime by
+ensuring that observations which violate the information-flow policy
+receive a view of the data computed without access to the secret
+inputs. Secure multi-execution has been extended in a variety of ways,
+e.g., scaling to its implementation in web browsers~\cite{Bielova:11},
+adding declassification in a granular way~\cite{Rafnsson:13}, and even
+preventing side-channel attacks~\cite{Kashyap:11}.
+
+As the number of principals increases, secure multi-execution's
+overhead increases exponentially, unnecessarily duplicating work not
+influenced by secret inputs. Austin et al. introduced faceted
+execution as an optimization of secure multi-execution
+in~\cite{Austin:2012}. Instead of treating the whole program as a
+potentially-secret computation, faceted execution realizes that
+influence can be tracked and propagated in a granular way using
+facets. Notably, Austin et al.'s work does not include first-class
+labels, as it was simulating secure multi-execution, where the
+principals could not be dynamically generated.
+
+At the same time, Yang et al. first implemented Jeeves, a language
+allowing policy-agnostic programming~\cite{Yang:2012}. Policy-agnostic
+programming takes the view that programs should be written without
+regard to a particular privacy policy, because as the policy changes,
+correctly updating program logic is cumbersome and
+error-prone. Policy-agnostic programming was first implemented in the
+domain-specific language Jeeves, using an SMT solver to decide which
+view of secret data to reveal based on a policy. Later, both authors
+collaborated to implement Jeeves using faceted
+execution.~\cite{Austin:2013}. This formulation includes first-class
+labels, and is the basis for our concrete semantics.
+
+Several other efforts into dynamic analysis for information flow are
+worth noting. \citet{Stefan:2011} first presented \code{LIO}---a monad
+(with implementation in Haskell) that tracks privilege of the current
+program counter and forbids effects that would violate the security
+policy. It might be surprising that \code{LIO}
+works well for Haskell programs, given that faceted execution is
+more precise than \code{LIO}---allowing values to become faceted
+rather than halting the program. One key difference is that Haskell
+programs emphasize purity while languages such as
+JavaScript (the original target of faceted execution) does not, so much
+of the machinery for faceted execution's effect on the store is less
+interesting. Several authors have implemented related systems to
+\code{LIO}, including variants of faceted execution \cite{Schmitz:2016}
+and variants of \code{LIO} that extend its
+power to arbitrary monad transformers~\cite{james}. We believe that it
+would be possible to implement a variant of our technique that would
+give similar insights to programs using \code{LIO}, though much of the
+interesting machinery for handling state may be unnecessary.
+
 \section{Conclusion}

### 2018-07-24 paper/paper.tex
making code smaller, I think..?
draft of conclusion

--- 2018-07-24 paper/paper.tex
@@
 \usepackage{xcolor}
-\usepackage[labelsep=quad,indention=10pt]{subfig}
 \usepackage{mathpartir} % Inference rules
@@
 faceted execution is much smaller than other systems: our core macros
-comprise roughly 170 source lines of Racket, with another 120 lines of
+comprise only 170 source lines of Racket, with another 120 lines of
 library code to perform various facet-related functions.
 
-\paragraph*{Case Study: Battleship in Racets}
-
-\begin{figure*}
-  \subfloat[]{%
-    \includegraphics[height=1.1in]{a.png}%
-    \label{fig:player1}%
-  } 
-  \quad
-  \subfloat[]{%
-    \includegraphics[height=1.1in]{b.png}%
-    \label{fig:player1player2}%
-  }
-  \quad
-  \subfloat[]{%
-    \includegraphics[height=.7in]{c.png}%
-    \label{fig:player2strike}%
-  }
-  \vspace{.3in}
-  \quad
-  \subfloat[]{%
-    \includegraphics[height=1.1in]{d.png}%
-    \label{fig:player1afterstrike}%
-  }
-  \caption{Screenshots from our Battleship case study.}
-  \label{fig:case}
-\end{figure*}
-
-To gain perspective on how Racets enables policy-agnostic programming,
-we scaled our implementation from Section~\ref{sec:overview} to a
-web-based game of Battleship written in Racets. Our implementation
-uses Racket's \texttt{web-server} framework~\cite{webserver}, which
-defines an API for writing HTTP-based server applications.
-
-Figure~\ref{fig:case} shows several screenshots of our Battleship
-application. The first screenshot~\ref{fig:player1} shows the board as
-viewed by player 1 (note the parameter \texttt{/player1/player1}),
-while the second shows the empty board observed when player 2 attempts
-to view player 1's board. The screenshot in~\ref{fig:player2strike}
-shows the response seen by player 2 upon a successful hit. Finally
-screenshot~\ref{fig:player1afterstrike} shows player one's board with
-the ship on \bmth{(3,2)} removed.
-
-When running, our game server provides several routes that a user can
-access:
-
-\begin{lstlisting}[language=Racket,escapechar=|,name=case]
-(define-values (dispatch generate-url)
-  (dispatch-rules
-    [("player1" (string-arg)) player1board]
-    [("player2" (string-arg)) player2board]
-    [("player1strike" (string-arg)) p1strike]
-    [("player2strike" (string-arg)) p2strike]))
-\end{lstlisting}
-
-The route \texttt{/player1/<id>} (or \texttt{/player2/<id>}) renders
-player 1's game board when viewed as \texttt{<id>}. We facet game
-boards with policies that reveal player 1's board when \texttt{<id>}
-is \texttt{player1}, and do the same with player 2:
-
-\begin{lstlisting}[language=Racket,escapechar=|,name=case]
-(define p1l (mkpol "player1"))
-(define p1board
-  (box (fac p1l
-            (add-pieces (makeboard) '(1 2 ldots))
-            (makeboard))))
-\end{lstlisting}
-
-The board is explicitly made into a box: this is because the board's
-state will change as player 2 makes moves and eliminates pieces from
-their board. The \code{player1board} function implements the logic to
-render player 1's board as an HTML table. The argument \code{viewer}
-corresponds to the \texttt{<id>} route argument, and is passed to
-\code{player1board} by the framework. This argument is then used to
-observe the board game
-
-\begin{lstlisting}[language=Racket,escapechar=|,name=case]
-(define player1board
-  (ext-lambda (request viewer)
-         (http-response "<h1>Player 1's Game Board</h1>"
-                        (pretty-print 
-                           (obs p1l name (deref p1board))))))
-\end{lstlisting}
-
-The implementation of \code{player1board} uses a special form
-\code{ext-lambda}, discussed at the end of this section, to allow code
-from Racets to be executed by the framework (which is not prepared to
-execute faceted code).
-
-The function \code{p1strike} allows player 1 to make a guess as to the
-position of ships on player 2's board. The function parses the
-position into two coordinates and then calls \code{mark-hit} to
-perform the hit, updating player 2's board and then observing the
-result to answer (to player 1) whether the result was a hit or not:
-
-\begin{lstlisting}[language=Racket,escapechar=|,name=case]
-(define p1strike
-  (ext-lambda
-   (request position)
-   (let* ([x (char-to-num (string-ref position 0))]
-          [y (char-to-num (string-ref position 2))]
-          [ans (mark-hit p2board x y)]
-      (set! p2board (car ans))
-      (http-response
-       (if (cdr (obs p2l "player2" ans)) |label{lineno:explicitobs}|
-           "<h1>Congratulations!</h1> <h4>You hit player 2!</h4>"
-           "<p>No hit :(</p>")))))))
-\end{lstlisting}
-
-Note that we need to use an explicit \code{obs} form on
-line~\ref{lineno:explicitobs}. This is because---as \code{p2board} is
-a facet---the result will also be a faceted value. When we want to
-display the output to player 1, our code needs to explicitly observe
-the answer, as \code{http-response} cannot accept a faceted value.
-
-\paragraph*{}
-
-\section{Conclusion}
+We plan to make our prototype of \racets available publicly.
+
+\section{Conclusion and Future Work}
 \label{sec:conclusion}
 
-asdf asdf
+In this paper, we have reviewed the operation of faceted execution, a linguistic paradigm
+enabling policy-agnostic programming, and showed how it may be implemented within
+the Racket programming system as a library of macros. As Racket macros permit core language
+forms (including function application, $\lambda$-abstraction, conditionals, mutation, etc.)
+to be rewritten arbitrarily, it is possible to rewrite the meaning of these forms to support
+a faceted semantics directly. We call our prototype system \racets: Racket with Facets.
+
+The advantage of this approach is that faceted, policy-agnostic, programs may be written
+directly in Racket, making use of the wealth of Racket code already available.
+A central challenge of this then, is how to ensure there is a sound and practical inter-operation
+between racets and standard Racket (or other languages written as libraries in Racket). Our
+approach to this has been to use a tagging scheme that identifies values from \racets
+so untagged values may be treated by \racets as originating from a non-\racets language.
+For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$
+form in \racets, can be automatically lifted to support FE (so that it can split when applied
+on a faceted value).
+
+Our hypothesis is that this tagging scheme is key to permitting inter-operation
+between \racets and Racket, and we have implemented a faceted, web-based game of Battleship
+to explore this idea. We suspect that a more thorough investigation of likely idioms
+for faceted, non-faceted module interaction is needed and that purely functional code
+plays a special role as a degenerate case where arbitrary non-faceted code may be lifted
+to operate over facted values without potential unsoundness. In the future, we plan to explore
+these design choices in a more principled way and also to scale a static analysis of faceted
+execution to fully expanded Racket so it may be applied directly to \racets.
 

### 2018-07-24 paper/paper.tex

--- 2018-07-24 paper/paper.tex
@@
 screenshot~\ref{fig:player1afterstrike} shows player one's board with
-the ship on \bmth{(3,2)} removed.
+the ship on \bmth{(2,3)} removed.
 
@@
 
-\section{Conclusion}
+\section{Conclusion and Future Work}
 \label{sec:conclusion}
 
-asdf asdf
+In this paper, we have reviewed the operation of faceted execution, a linguistic paradigm
+enabling policy-agnostic programming, and showed how it may be implemented within
+the Racket programming system as a library of macros. As Racket macros permit core language
+forms (including function application, $\lambda$-abstraction, conditionals, mutation, etc.)
+to be rewritten arbitrarily, it is possible to rewrite the meaning of these forms to support
+a faceted semantics directly. We call our prototype system \racets: Racket with Facets.
+
+The advantage of this approach is that faceted, policy-agnostic, programs may be written
+directly in Racket, making use of the wealth of Racket code already available.
+A central challenge of this then, is how to ensure there is a sound and practical inter-operation
+between racets and standard Racket (or other languages written as libraries in Racket). Our
+approach to this has been to use a tagging scheme that identifies values from \racets
+so untagged values may be treated by \racets as originating from a non-\racets language.
+For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$
+form in \racets, can be automatically lifted to support FE (so that it can split when applied
+on a faceted value).
+
+Our hypothesis is that this tagging scheme is key to permitting inter-operation
+between \racets and Racket, and we have implemented a faceted, web-based game of Battleship
+to explore this idea. We suspect that a more thorough investigation of likely idioms
+for faceted, non-faceted module interaction is needed and that purely functional code
+plays a special role as a degenerate case where arbitrary non-faceted code may be lifted
+to operate over facted values without potential unsoundness. In the future, we plan to explore
+these design choices in a more principled way and also to scale a static analysis of faceted
+execution to fully expanded Racket so it may be applied directly to \racets.
 

### 2018-07-24 paper/paper.tex
merging

--- 2018-07-24 paper/paper.tex
@@
 Because the applied function can be stateful, faceted execution also
-maintains the current privilege level in a \emph{program counter} (PC). The
+vmaintains the current privilege level in a \emph{program counter} (PC). The
 program counter is a property of the current evaluation context and is used
@@
 
+After making various moves, we eventually want to reveal the game
+boards, pulling the positive view out of \code{alice-board} to display
+Alice's board. To do this, we must \emph{observe} the facet with an
+\code{obs} form. Because Alice's board is faceted with
+\code{alice-label}, we specify that we want to observe
+\code{alice-label} and pass in an argument to that label showing that
+Alice is indeed the person observing the facet:
+
+\begin{lstlisting}[language=Racket,escapechar=|,name=example]
+(obs alice-label 1 alice-board) ; Returns Alice's board
+\end{lstlisting}
+
+If we had passed any value other than $1$ into the \code{obs} form,
+Alice's policy would return \code{false}. In this case, the \code{obs}
+form would reduce to $\blue{\star}$, and the program would fail
+(indicating that someone other than Alice attempted to view her
+board).
+
 \section{A Formal Semantics for Faceted Execution}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{displaymath}
@@
 \end{displaymath}
+\caption{Syntax of \lang.}
 \label{fig:syntax}
-\caption{Syntax of \lang. Forms unique to facets are shown in \fcol{red}.}
-\end{figure}
+\end{figure*}
 

### 2018-07-24 paper/paper.tex
tweak

--- 2018-07-24 paper/paper.tex
@@
 forms (including function application, $\lambda$-abstraction, conditionals, mutation, etc.)
-to be rewritten arbitrarily, it is possible to rewrite the meaning of these forms to support
+to be rewritten arbitrarily, it is possible to modify the meaning of these forms to support
 a faceted semantics directly. We call our prototype system \racets: Racket with Facets.

### 2018-07-24 paper/paper.tex
removing comment

--- 2018-07-24 paper/paper.tex
@@
 
-\kris{TODO: FIX THIS (make consistent w semantics)}
 \[\small
@@
                 \boxed{\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
-                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
-                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 \and
+                e_2, \rho, \sigma' \Downarrow_{pc \cup \{+\ell\}}^E \sigma'', v_1 \\\\
+                e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-\ell\}}^E \sigma''', v_2 \and
                 v = \formfacet{pc}{v_1}{v_2}}
               {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
-
 \end{array}

### 2018-07-24 paper/paper.tex
tweak

--- 2018-07-24 paper/paper.tex
@@
 A central challenge of this then, is how to ensure there is a sound and practical inter-operation
-between racets and standard Racket (or other languages written as libraries in Racket). Our
+between \racets and standard Racket (or other languages written as libraries in Racket). Our
 approach to this has been to use a tagging scheme that identifies values from \racets

### 2018-07-24 paper/paper.tex
related work title
tweak

@@
 
-\section{Related Work and Future Directions}
+\section{Related Work}
+\label{sec:related}
 
@@
 directly in Racket, making use of the wealth of Racket code already available.
-A central challenge of this then, is how to ensure there is a sound and practical inter-operation
-between \racets and standard Racket (or other languages written as libraries in Racket). Our
-approach to this has been to use a tagging scheme that identifies values from \racets
-so untagged values may be treated by \racets as originating from a non-\racets language.
+A central challenge of this then, is how to ensure there is a sound (w.r.t. secure multi-execution)
+and practical inter-operation between \racets and standard Racket (or other languages written as
+libraries in Racket). Our approach to this has been to use a tagging scheme that identifies values
+from \racets so untagged values may be treated by \racets as originating from a non-\racets language.
 For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$

### 2018-07-24 paper/paper.tex
adding paragraph on faceted interactions

--- 2018-07-24 paper/paper.tex
@@
 
-\paragraph*{}
+\paragraph*{Module Interactions in \racets}
+
+There is a wealth of existing Racket code we might like to incorporate
+into \racets programs. For example, our case study uses the
+\texttt{web-server} framework for building web applications. However,
+in general, we believe that interacting with code not written using
+faceted execution is a challenging open problem, and we do not know of any
+principled solutions in the literature.
+
+One immediate problem in \racets is how to pass functions from \racets
+to plain Racket code. For example, the \texttt{web-server} framework
+is written in Racket, and does not know how to call tagged closures
+from \racets. As a stopgap, we added an \code{ext-lambda} form to
+\racets. This form allows creating a Racket-style lambda in Racets
+that will be used by functions in other modules, necessary for the
+implementation of our case study.
+
+We plan to explore interactions with unfaceted code more in the
+future, and believe it will an exciting direction. For example, once
+execution escapes \racets, we have no guarantee that the privacy
+policy won't be violated. One solution may be to implicitly perform an
+\code{obs} based on the current \rmth{pc} at points where \racets
+interacts with unfaceted modules. But we do not fully understand the
+ramifications or ergonomics of this choice, and suspect there may be a
+wide array of design choices to handle these module interactions
+including security type systems and blame (to track which module
+violated the privacy policy).
 

### 2018-07-24 paper/paper.tex

@@
 directly in Racket, making use of the wealth of Racket code already available.
-A central challenge of this then, is how to ensure there is a sound and practical inter-operation
-between racets and standard Racket (or other languages written as libraries in Racket). Our
-approach to this has been to use a tagging scheme that identifies values from \racets
-so untagged values may be treated by \racets as originating from a non-\racets language.
+A central challenge of this then, is how to ensure there is a sound (w.r.t. secure multi-execution)
+and practical inter-operation between \racets and standard Racket (or other languages written as
+libraries in Racket). Our approach to this has been to use a tagging scheme that identifies values
+from \racets so untagged values may be treated by \racets as originating from a non-\racets language.
 For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$

### 2018-07-24 paper/paper.tex
pass through paper fixing up comments and undefined refs

@@
   \code{if}, though it may be obtained via a Church encoding if
-  desired as in Austin et al.\cite{Austin:12}. Our implementation
+  desired as in Austin et al.\cite{Austin:2012}. Our implementation
   includes \code{if} but not other constructs such as \code{cond}}:
@@
 being observed may appear arbitrarily deep in the facet (or not at
-all). \zw{We elide the description of the meta-function \rmth{\var{obs}}
-here, but it is fully described in Austin et al.~\cite{Austin:2012}}
+all). As our implementation of \rmth{\var{obs}} is unchanged from its
+definition in~\cite{Austin:2012}, we elide it here.
 
@@
 consider the case under which a facet is used when an address is
-expected. \zw{The role of the \textit{write} metafunction is to 
-recursively dig into faceted value, and make writes to the addresses.
-If it is an address at the beginning, which hits the base case,
-the \textit{write} metafunction constructs a new faceted value according
-to \bmth{pc} and makes modification to the address.}
+expected.
 
@@
 application. The first screenshot~\ref{fig:player1} shows the board as
-viewed by player 1 (note the parameter \texttt{/player1/player1}),
+viewed by player 1 (using the route \texttt{/player1/player1}),
 while the second shows the empty board observed when player 2 attempts
@@
       (http-response
-       (if (cdr (obs p2l "player2" ans)) |label{lineno:explicitobs}|
+       (if (cdr (obs p2l "player2" ans))
            "<h1>Congratulations!</h1> <h4>You hit player 2!</h4>"
@@
 Note that we need to use an explicit \code{obs} form on
-line~\ref{lineno:explicitobs}. This is because---as \code{p2board} is
+line 25. This is because---as \code{p2board} is
 a facet---the result will also be a faceted value. When we want to

### 2018-07-24 paper/paper.tex
abstract draft

--- 2018-07-24 paper/paper.tex
@@
 
-\title{\racets: Policy{-}Agnostic Programming in Racket}
+\title{\racets: Faceted Execution in Racket}
 
@@
 
-\begin{abstract}lorem ipsum...\end{abstract}
-
 %% \begin{CCSXML}
@@
 %% \ccsdesc[100]{Networks~Network reliability}
+
+\begin{abstract}
+  Faceted execution is a linguistic paradigm for dynamic information-flow
+  control with the distinguishing feature that some program values may be
+  \emph{faceted}. Faceted values simulate multiple executions (for different
+  combinations of security labels) at once. This enables policy-agnostic programming:
+  a style of programming where information-flow policies are stated independently
+  of core program logic and are then enforced at runtime by a dynamic monitor. This
+  approach enforces privacy constraints without requiring systems to be updated at every
+  relevant code-point whenever a privacy policy needs to be added or changed.
+
+  In this paper, we present \racets: an implementation of faceted execution for
+  core language features such as application, mutation, and conditionals, using
+  Racket's macro system. As Racket permits even core forms to be instrumented
+  or rewritten arbitrarily, we are able to design a library of macros for 
+  faceted execution in Scheme. We review faceted execution, formalize its operation,
+  show how these big-step rules are turned into macros, and then discuss
+  issues of interoperability with non-faceted Racket code.
+\end{abstract}
 

### 2018-07-24 paper/paper.tex
abstract

--- 2018-07-24 paper/paper.tex
@@
 
-\begin{abstract}lorem ipsum...\end{abstract}
+\begin{abstract}
+Faceted Execution (FE) is a linguistic paradigm for dynamic
+information flow control. Using faceted execution, secure program data
+is represented by \emph{facets}: decision trees that encode how the
+data should appear to its owner (represented by a label) versus everyone
+else. When labels are allowed to be first-class (i.e., predicates that
+decide at runtime which data to reveal), faceted execution enables
+\emph{policy-agnostic programming}: a programming style that allows
+privacy policies for data to be enforced independently of code that
+computes on that data.
+
+To date, implementations of faceted execution are relatively
+heavyweight: requiring either changing the language runtime or the
+application code (e.g., by using monads). In this paper, we present
+\racets: an extension of Racket to faceted execution via macros. Given
+Racket's highly-expressive macro system, our implementation follows
+relatively directly from the semantics of faceted execution. To
+demonstrate how \racets can be used for policy-agnostic programming,
+we use it to build a web-based game of Battleship. Our implementation
+sheds light on several interesting issues in interacting with code
+written without faceted execution. \racets is currently available
+under an open-source license on GitHub.
+
+\end{abstract}
 

### 2018-07-24 paper/paper.tex
addnig blurb to abstract on lal
abstract tweaks

@@
 \begin{abstract}
-Faceted Execution (FE) is a linguistic paradigm for dynamic
-information flow control. Using faceted execution, secure program data
-is represented by \emph{facets}: decision trees that encode how the
+Faceted Execution is a linguistic paradigm for dynamic
+information-flow control. Under faceted execution, secure program data
+is represented by \emph{faceted} values: decision trees that encode how the
 data should appear to its owner (represented by a label) versus everyone
@@
 application code (e.g., by using monads). In this paper, we present
-\racets: an extension of Racket to faceted execution via macros. Given
-Racket's highly-expressive macro system, our implementation follows
-relatively directly from the semantics of faceted execution. To
-demonstrate how \racets can be used for policy-agnostic programming,
-we use it to build a web-based game of Battleship. Our implementation
-sheds light on several interesting issues in interacting with code
-written without faceted execution. \racets is currently available
-under an open-source license on GitHub.
-
+\racets: an extension of Racket to faceted execution a library of
+macros. Given Racket's highly-expressive macro system, our
+implementation follows relatively directly from the semantics of
+faceted execution. To demonstrate how \racets can be used for
+policy-agnostic programming, we use it to build a web-based game of
+Battleship. Our implementation sheds light on several interesting
+issues in interacting with code written without faceted execution. Our
+\racets implementation is open source, under development, and
+available online.
 \end{abstract}

### 2018-07-24 paper/paper.tex
spell check

--- 2018-07-24 paper/paper.tex
@@
 heavyweight: requiring either changing the language runtime or the
-application code (e.g., by using monads). In this paper, we present
-\racets: an extension of Racket to faceted execution via macros. Given
-Racket's highly-expressive macro system, our implementation follows
-relatively directly from the semantics of faceted execution. To
-demonstrate how \racets can be used for policy-agnostic programming,
-we use it to build a web-based game of Battleship. Our implementation
-sheds light on several interesting issues in interacting with code
-written without faceted execution. \racets is currently available
-under an open-source license on GitHub.
-
+application code (e.g., by using monads). Following Racket's
+languages-as-libraries approach, we present Racets: an implementation
+of faceted execution as a library of macros.  Given Racket's
+highly-expressive macro system, our implementation follows relatively
+directly from the semantics of faceted execution. To demonstrate how
+\racets can be used for policy-agnostic programming, we use it to
+build a web-based game of Battleship. Our implementation sheds light
+on several interesting issues in interacting with code written without
+faceted execution. Our \racets implementation is open source, under
+development, and available online.
 \end{abstract}
@@
 of first-class security labels, tracking an arbitrary number of
-facets per value, and keeping facted-value trees in a canonical order,
+facets per value, and keeping faceted-value trees in a canonical order,
 are all central challenges in any practical implementation. For example, the
@@
 with code written in the host language. By contrast, Scheme boasts a powerful
-hygenic macro system that allows essentially any linguistic form
+hygienic macro system that allows essentially any linguistic form
 to be modified arbitrarily.
@@
 programming in Racket via macros. \racets provides facilities for
-creating policies and faceting secure data with those policies. \racets
-also extends several core forms in Racket to work with faceted
-values (our implementation is detailed in Section~\ref{sec:implementation}). We
-have measured the overhead of \racets in several microbenchmarks, and
-have used \racets to implement a small server-based
-board-game (detailed in Sections~\ref{sec:overview} and~\ref{sec:implementation}). We see \racets as a
-promising prototype for policy-agnostic programming in Racket, and
-conclude with discussion of future directions in Section~\ref{sec:conclusion}.
+creating policies and faceting secure data with those
+policies. \racets also extends several core forms in Racket to work
+with faceted values (our implementation is detailed in
+Section~\ref{sec:implementation}). We have used \racets to implement a
+small server-based board-game (detailed in Sections~\ref{sec:overview}
+and~\ref{sec:implementation}). Relevant related work is presented in
+section~\ref{sec:related}. We see \racets as a promising prototype for
+policy-agnostic programming in Racket, and conclude with discussion of
+future directions in Section~\ref{sec:conclusion}.
 
@@
 board. If the guess is successful the tile is removed from the
-board and a hit is declared publically. Play ends once one player's board
+board and a hit is declared publicly. Play ends once one player's board
 has no remaining tiles, at which point that player loses.
@@
 The $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ \blue{e_\text{fac}}\code{)}$ form takes
-a label, a key, and a facted value. Explicit observation projects a single label
+a label, a key, and a faceted value. Explicit observation projects a single label
 $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ to either its positive or negative facet,
@@
 Because the applied function can be stateful, faceted execution also
-vmaintains the current privilege level in a \emph{program counter} (PC). The
+maintains the current privilege level in a \emph{program counter} (PC). The
 program counter is a property of the current evaluation context and is used
@@
 and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
-not make this faceting explicit, a senstive value could leak from one PC to another.
+not make this faceting explicit, a sensitive value could leak from one PC to another.
 We expand upon these subtleties in Section~\ref{sec:semantics},
@@
 meta-functions to do their work. This is because box creation, reads,
-and writes may occur within a privilaged context, and care must be
+and writes may occur within a privileged context, and care must be
 taken to form facets when \rmth{pc} is nonempty. To understand why,
@@
 Figure~\ref{fig:semantics}, which we recapitulate here in three
-distint colors for each case:
+distinct colors for each case:
 
@@
 plays a special role as a degenerate case where arbitrary non-faceted code may be lifted
-to operate over facted values without potential unsoundness. In the future, we plan to explore
+to operate over faceted values without potential unsoundness. In the future, we plan to explore
 these design choices in a more principled way and also to scale a static analysis of faceted

### 2018-07-24 paper/paper.tex
taking out potentialy
adding cites to hygienic macros

@@
 
-\emph{Faceted execution} (FE) is a highly expressive (but potentially expensive)
+\emph{Faceted execution} (FE) is a highly expressive 
 language semantics enabling policy-agnostic programming. In FE, dynamic information-flow
@@
 In this paper we present \racets, an implementation of policy-agnostic
-programming in Racket via macros. \racets provides facilities for
+programming in Racket via macros~\cite{Kohlbecker:1986, Dybvig:1992}. \racets provides facilities for
 creating policies and faceting secure data with those
@@
 The semantics of faceted execution is an extension of the lambda
-calculus, leading to a natural question: can we use Racket's macros to
+calculus, leading to a natural question: can we use Racket's macros~\cite{Kohlbecker:1986, Dybvig:1992} to
 extend Racket to faceted execution? We will see that the answer is

### 2018-07-24 paper/paper.tex
adding fac cite
self-cite

--- 2018-07-24 paper/paper.tex
@@
 heavyweight: requiring either changing the language runtime or the
-application code (e.g., by using monads). Following Racket's
-languages-as-libraries approach, we present Racets: an implementation
-of faceted execution as a library of macros.  Given Racket's
-highly-expressive macro system, our implementation follows relatively
-directly from the semantics of faceted execution. To demonstrate how
-\racets can be used for policy-agnostic programming, we use it to
-build a web-based game of Battleship. Our implementation sheds light
-on several interesting issues in interacting with code written without
-faceted execution. Our \racets implementation is open source, under
-development, and available online.
+application code (e.g., by using monads). In this paper, we present
+\racets: an extension of Racket to faceted execution a library of
+macros. Given Racket's highly-expressive macro system, our
+implementation follows relatively directly from the semantics of
+faceted execution. To demonstrate how \racets can be used for
+policy-agnostic programming, we use it to build a web-based game of
+Battleship. Our implementation sheds light on several interesting
+issues in interacting with code written without faceted execution. Our
+\racets implementation is open source, under development, and
+available online.
 \end{abstract}
@@
 of first-class security labels, tracking an arbitrary number of
-facets per value, and keeping faceted-value trees in a canonical order,
+facets per value, and keeping facted-value trees in a canonical order,
 are all central challenges in any practical implementation. For example, the
@@
 with code written in the host language. By contrast, Scheme boasts a powerful
-hygienic macro system that allows essentially any linguistic form
+hygenic macro system that allows essentially any linguistic form
 to be modified arbitrarily.
@@
 programming in Racket via macros. \racets provides facilities for
-creating policies and faceting secure data with those
-policies. \racets also extends several core forms in Racket to work
-with faceted values (our implementation is detailed in
-Section~\ref{sec:implementation}). We have used \racets to implement a
-small server-based board-game (detailed in Sections~\ref{sec:overview}
-and~\ref{sec:implementation}). Relevant related work is presented in
-section~\ref{sec:related}. We see \racets as a promising prototype for
-policy-agnostic programming in Racket, and conclude with discussion of
-future directions in Section~\ref{sec:conclusion}.
+creating policies and faceting secure data with those policies. \racets
+also extends several core forms in Racket to work with faceted
+values (our implementation is detailed in Section~\ref{sec:implementation}). We
+have measured the overhead of \racets in several microbenchmarks, and
+have used \racets to implement a small server-based
+board-game (detailed in Sections~\ref{sec:overview} and~\ref{sec:implementation}). We see \racets as a
+promising prototype for policy-agnostic programming in Racket, and
+conclude with discussion of future directions in Section~\ref{sec:conclusion}.
 
@@
 board. If the guess is successful the tile is removed from the
-board and a hit is declared publicly. Play ends once one player's board
+board and a hit is declared publically. Play ends once one player's board
 has no remaining tiles, at which point that player loses.
@@
 The $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ \blue{e_\text{fac}}\code{)}$ form takes
-a label, a key, and a faceted value. Explicit observation projects a single label
+a label, a key, and a facted value. Explicit observation projects a single label
 $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ to either its positive or negative facet,
@@
 and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
-not make this faceting explicit, a sensitive value could leak from one PC to another.
+not make this faceting explicit, a senstive value could leak from one PC to another.
 We expand upon these subtleties in Section~\ref{sec:semantics},
@@
 
-Our semantics is shown in Figure~\ref{fig:semantics}. As \lang is an
+Our semantics is shown in Figure~\ref{fig:semantics} \cite{Micinski:2019}.
+As \lang is an
 extension of the lambda calculus with references, we present the parts
@@
 meta-functions to do their work. This is because box creation, reads,
-and writes may occur within a privileged context, and care must be
+and writes may occur within a privilaged context, and care must be
 taken to form facets when \rmth{pc} is nonempty. To understand why,
@@
 Figure~\ref{fig:semantics}, which we recapitulate here in three
-distinct colors for each case:
+distint colors for each case:
 
@@
 plays a special role as a degenerate case where arbitrary non-faceted code may be lifted
-to operate over faceted values without potential unsoundness. In the future, we plan to explore
-these design choices in a more principled way and also to scale a static analysis of faceted
-execution to fully expanded Racket so it may be applied directly to \racets.
+to operate over facted values without potential unsoundness. In the future, we plan to explore
+these design choices in a more principled way and also to scale a static analysis \cite{Micinski:2019}
+of faceted execution to fully expanded Racket so it may be applied directly to \racets.
 

### 2018-07-24 paper/paper.tex

--- 2018-07-24 paper/paper.tex
@@
 \emph{Faceted execution} (FE) is a highly expressive 
-language semantics enabling policy-agnostic programming. In FE, dynamic information-flow
+language semantics enabling policy-agnostic programming~\cite{Austin:2012}. In FE, dynamic information-flow
 monitors instrument the program, encoding sensitive values as \emph{faceted values}:

### 2018-07-24 paper/paper.tex
add a sentence to sec2

@@
 \emph{label} to protect their data. A label is unique id mapped to a policy predicate
-that takes an key (e.g., the current user's name) and returns true or false to indicate
-permission for the label. Alice's label is used to annotate data she wants
+that takes a key (e.g., the current user's name) and returns true or false to indicate
+permission for the label. Alice's label is used to annotate the data she wants
 to be kept secret. Supposing Alice chooses to be player 1, she may use the
@@
 In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
-to ensure execution will fail if Bob tries to observe Alice's secret gameboard.
-The $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ \blue{e_\text{fac}}\code{)}$ form takes
-a label, a key, and a faceted value. Explicit observation projects a single label
-$\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ to either its positive or negative facet,
-depending on whether the policy associated with $\blue{e_\ell}$ returns true for key
-$\blue{e_\text{key}}$. If Bob tries to observe Alice's board, the policy predicate
-will return false (from \texttt{(= 1 $\blue{2}$)}) and Alice's negative facet $\blue{\star}$ will result.
+to ensure execution will fail if Bob tries to observe Alice's secret gameboard. To observe
+Alice's gameboard, Bob can try to use $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ 
+\blue{e_\text{fac}}\code{)}$ form, which takes a label, a key, and a faceted value.
+Explicit observation projects a single label $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
+to either its positive or negative facet, depending on whether the policy associated 
+with $\blue{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
+Alice's board, the policy predicate will return false (from \texttt{(= 1 $\blue{2}$)}) 
+and Alice's negative facet $\blue{\star}$ will result.
 

### 2018-07-24 paper/paper.tex
removing some obs stuff
spell check for sec2 done

@@
 
-In other applications, Alice might choose a sensible default value to
+In other applications, Alice may choose a sensible default value to
 reveal to others---she may even want to create a \emph{nested}
-facet. For example, a social-networking application might use a
+facet. For example, a social-networking application may use a
 nested facet consisting of two labels for
 \blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
-could then present three views of her social-media profile: \bmth{p_1} to
+can then present three views of her social-media profile: \bmth{p_1} to
 her family, containing her phone number and other contact information,
@@
 cannot be leaked from the secure context (speculative execution under the
-$\blue{+\ell}$ facet). This is because, for the duration of the the app ``split'',
+$\blue{+\ell}$ facet). This is because, for the duration of the app ``split'',
 the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
 and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
-not make this faceting explicit, a sensitive value could leak from one PC to another.
+not make this faceting explicit, a sensitive value can leak from one PC to another.
 We expand upon these subtleties in Section~\ref{sec:semantics},
@@
 \end{lstlisting}
-
-If we had passed any value other than $1$ into the \code{obs} form,
-Alice's policy would return \code{false}. In this case, the \code{obs}
-form would reduce to $\blue{\star}$, and the program would fail
-(indicating that someone other than Alice attempted to view her
-board).
 
@@
 mechanisms (such as continuation marks\kris{cite}, to which parameters
-macro-expand) could also be used. \racets defines the parameter
+macro-expand) can also be used. \racets defines the parameter
 \code{current-pc}, and updates it as computation progresses:
@@
 
-There is a wealth of existing Racket code we might like to incorporate
+There is a wealth of existing Racket code we may like to incorporate
 into \racets programs. For example, our case study uses the
@@
 program counter and forbids effects that would violate the security
-policy. It might be surprising that \code{LIO}
+policy. It may be surprising that \code{LIO}
 works well for Haskell programs, given that faceted execution is

### 2018-07-24 paper/paper.tex
fixing colors

--- 2018-07-24 paper/paper.tex
@@
 %% To color math, put it in an \mc command, e.g., \mc{$a$}
-\newcommand{\colorMATH}{black!20!blue}
+\definecolor{colorMATH}{HTML}{3E5BA9}
+\definecolor{colorFAC}{HTML}{9F1D20}
 \newcommand{\colorID}{black!20!blue}
-\newcommand{\colorCOMM}{0.133,0.545,0.133}
-\newcommand{\colorFAC}{black!20!red}
-\newcommand{\blue}[1] {{\color{\colorMATH} #1}}
-\newcommand{\fcol}[1] {{\color{\colorFAC} #1}}
-\newcommand{\bmth}[1] {{\color{\colorMATH} $#1$}}
-\newcommand{\rmth}[1] {{\color{\colorFAC} $#1$}}
+\newcommand{\blue}[1] {{\color{colorMATH} #1}}
+\newcommand{\fcol}[1] {{\color{colorFAC} #1}}
+\newcommand{\bmth}[1] {{\color{colorMATH} $#1$}}
+\newcommand{\rmth}[1] {{\color{colorFAC} $#1$}}
 \newcommand{\code}[1]{\lstinline{#1}}
@@
 
-If we had passed any value other than $1$ into the \code{obs} form,
-Alice's policy would return \code{false}. In this case, the \code{obs}
-form would reduce to $\blue{\star}$, and the program would fail
-(indicating that someone other than Alice attempted to view her
-board).
-
 \section{A Formal Semantics for Faceted Execution}
@@
         \begingroup
-        \color{\colorMATH}
+        \color{colorMATH}
         \begin{array}{cccc}
@@
         \begingroup
-        \color{\colorMATH}
+        \color{colorMATH}
         \begin{array}{ccc}
@@
        \begin{array}{ccc}
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{Fac-Create-Split}]
@@
           & 
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{Fac-Create-Pos}]
@@
           & 
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{Fac-Create-Neg}]
@@
     \begin{array}{cc}
-      {\color{\colorFAC}
+      {\color{colorFAC}
         \inferrule[\textsc{Let-Label}]
@@
           & 
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{Obs}]
@@
     \begingroup
-    \color{\colorMATH}
+    \color{colorMATH}
     \begin{displaymath}
@@
         \begin{array}{ccc}
-          {\color{\colorMATH}
+          {\color{colorMATH}
           \inferrule[\textsc{App-$\star$}]
@@
           & 
-          {\color{\colorMATH}
+          {\color{colorMATH}
           \inferrule[\textsc{App-Base}]
@@
           & 
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{App-Split}]
@@
         \\\\
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{App-Facet-Pos}]
@@
           & 
-          {\color{\colorFAC}
+          {\color{colorFAC}
           \inferrule[\textsc{App-Facet-Neg}]
@@
            (if (box? var)
-               ; <@$\color[rgb]{\colorCOMM}\var{write}(\sigma, \alpha, pc, v)$@>
+               ; <@$\color{colorFAC}\var{write}(\sigma, \alpha, pc, v)$@>
                (set-box! var (construct-facet (current-pc) v (unbox var)))
@@
                  (facet-labelname (unbox var))
-                 ; <@$\color[rgb]{\colorCOMM}\var{write}(\sigma, \alpha, pc \cup \{+l\}, v)$@>
+                 ; <@$\color{colorFAC}\var{write}(\sigma, \alpha, pc \cup \{+l\}, v)$@>
                  (write
@@
                    (set-add pc (pos (facet-labelname var))))
-                 ; <@$\color[rgb]{\colorCOMM}\var{write}(\sigma, \alpha, pc \cup \{-l\}, v)$@>
+                 ; <@$\color{colorFAC}\var{write}(\sigma, \alpha, pc \cup \{-l\}, v)$@>
                  (write

### 2018-07-24 paper/paper.tex
colors for ell

--- 2018-07-24 paper/paper.tex
@@
 \emph{label} to protect their data. A label is unique id mapped to a policy predicate
-that takes a key (e.g., the current user's name) and returns true or false to indicate
-permission for the label. Alice's label is used to annotate the data she wants
+that takes an key (e.g., the current user's name) and returns true or false to indicate
+permission for the label. Alice's label is used to annotate data she wants
 to be kept secret. Supposing Alice chooses to be player 1, she may use the
@@
 Bob would use a similar policy (but for player $2$ instead of $1$). At runtime,
-the \code{let-label} form creates a label \blue{$\ell_{A}$} and binds
+the \code{let-label} form creates a label \fcol{$\ell_{A}$} and binds
 it to a closure for its policy predicate. When Alice wants to protect a
@@
 In the above example, \blue{$\star$} (lazy failure) is used in the negative branch
-to ensure execution will fail if Bob tries to observe Alice's secret gameboard. To observe
-Alice's gameboard, Bob can try to use $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ 
-\blue{e_\text{fac}}\code{)}$ form, which takes a label, a key, and a faceted value.
-Explicit observation projects a single label $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
-to either its positive or negative facet, depending on whether the policy associated 
-with $\blue{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
-Alice's board, the policy predicate will return false (from \texttt{(= 1 $\blue{2}$)}) 
-and Alice's negative facet $\blue{\star}$ will result.
-
-In other applications, Alice may choose a sensible default value to
+to ensure execution will fail if Bob tries to observe Alice's secret gameboard.
+The $\code{(obs}\ \fcol{e_\ell}\ \blue{e_\text{key}}\ \blue{e_\text{fac}}\code{)}$ form takes
+a label, a key, and a faceted value. Explicit observation projects a single label
+$\fcol{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ to either its positive or negative facet,
+depending on whether the policy associated with $\fcol{e_\ell}$ returns true for key
+$\blue{e_\text{key}}$. If Bob tries to observe Alice's board, the policy predicate
+will return false (from \texttt{(= 1 $\blue{2}$)}) and Alice's negative facet $\blue{\star}$ will result.
+
+In other applications, Alice might choose a sensible default value to
 reveal to others---she may even want to create a \emph{nested}
-facet. For example, a social-networking application may use a
+facet. For example, a social-networking application might use a
 nested facet consisting of two labels for
-\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
-can then present three views of her social-media profile: \bmth{p_1} to
+\fcol{$\ell_{\text{Friends}}$} and \fcol{$\ell_{\text{Family}}$}. A user
+could then present three views of her social-media profile: \bmth{p_1} to
 her family, containing her phone number and other contact information,
@@
 For example, if a stateful function ``splits'' when applied on both the positive and negative
-facets of a value faceted by a label $\blue{\ell}$, and on the positive branch
+facets of a value faceted by a label $\fcol{\ell}$, and on the positive branch
 the function uses $\texttt{set!}$ to mutate a variable $x$ from $2$ to $3$,
@@
 cannot be leaked from the secure context (speculative execution under the
-$\blue{+\ell}$ facet). This is because, for the duration of the app ``split'',
-the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
-and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
-not make this faceting explicit, a sensitive value can leak from one PC to another.
+$\fcol{+\ell}$ facet). This is because, for the duration of the the app ``split'',
+the evaluation context records that all values are implicitly guarded by $\fcol{+\ell}$
+and then $\fcol{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
+not make this faceting explicit, a sensitive value could leak from one PC to another.
 We expand upon these subtleties in Section~\ref{sec:semantics},
@@
 \end{lstlisting}
+
+If we had passed any value other than $1$ into the \code{obs} form,
+Alice's policy would return \code{false}. In this case, the \code{obs}
+form would reduce to $\blue{\star}$, and the program would fail
+(indicating that someone other than Alice attempted to view her
+board).
 
@@
 context. For example, to apply a faceted function to a value (as in
-the application of \bmth{\facet{\ell}{\lambda x.~0}{\lambda x.~1}}),
+the application of $\facet{\ell}{\blue{\lambda x.~0}}{\blue{\lambda x.~1}}$),
 the semantics first applies \bmth{\lambda x.~0} while extending \rmth{pc}
@@
 mechanisms (such as continuation marks\kris{cite}, to which parameters
-macro-expand) can also be used. \racets defines the parameter
+macro-expand) could also be used. \racets defines the parameter
 \code{current-pc}, and updates it as computation progresses:
@@
 
-There is a wealth of existing Racket code we may like to incorporate
+There is a wealth of existing Racket code we might like to incorporate
 into \racets programs. For example, our case study uses the
@@
 program counter and forbids effects that would violate the security
-policy. It may be surprising that \code{LIO}
+policy. It might be surprising that \code{LIO}
 works well for Haskell programs, given that faceted execution is

### 2018-07-24 paper/paper.tex

--- 2018-07-24 paper/paper.tex
@@
 to ensure execution will fail if Bob tries to observe Alice's secret gameboard. To observe
-Alice's gameboard, Bob can try to use $\code{(obs}\ \blue{e_\ell}\ \blue{e_\text{key}}\ 
+Alice's gameboard, Bob can try to use $\code{(obs}\ \fcol{e_\ell}\ \blue{e_\text{key}}\ 
 \blue{e_\text{fac}}\code{)}$ form, which takes a label, a key, and a faceted value.
-Explicit observation projects a single label $\blue{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
+Explicit observation projects a single label $\fcol{e_\ell}$ in faceted value $\blue{e_\text{fac}}$ 
 to either its positive or negative facet, depending on whether the policy associated 
-with $\blue{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
+with $\fcol{e_\ell}$ returns true for key $\blue{e_\text{key}}$. If Bob tries to observe 
 Alice's board, the policy predicate will return false (from \texttt{(= 1 $\blue{2}$)}) 
@@
 nested facet consisting of two labels for
-\blue{$\ell_{\text{Friends}}$} and \blue{$\ell_{\text{Family}}$}. A user
+\rmth{\ell_{\text{Friends}}} and \rmth{\ell_{\text{Family}}}. A user
 can then present three views of her social-media profile: \bmth{p_1} to
@@
 cannot be leaked from the secure context (speculative execution under the
-$\blue{+\ell}$ facet). This is because, for the duration of the app ``split'',
-the evaluation context records that all values are implicitly guarded by $\blue{+\ell}$
-and then $\blue{-\ell}$, respectively. If the semantics for $\texttt{set!}$ does
+\rmth{+\ell} facet). This is because, for the duration of the app ``split'',
+the evaluation context records that all values are implicitly guarded by \rmth{+\ell}
+and then \rmth{-\ell}, respectively. If the semantics for $\texttt{set!}$ does
 not make this faceting explicit, a sensitive value can leak from one PC to another.

### 2018-07-24 paper/paper.tex
adding cite

--- 2018-07-24 paper/paper.tex
@@
 counter. Our implementation uses Racket's parameters, though other
-mechanisms (such as continuation marks\kris{cite}, to which parameters
+mechanisms (such as continuation marks~\cite{Clements:2001}, to which parameters
 macro-expand) can also be used. \racets defines the parameter

### 2018-07-24 paper/paper.tex
added c-m cite

--- 2018-07-24 paper/paper.tex
@@
 counter. Our implementation uses Racket's parameters, though other
-mechanisms (such as continuation marks\kris{cite}, to which parameters
+mechanisms (such as continuation marks~\cite{clements2001modeling}, to which parameters
 macro-expand) can also be used. \racets defines the parameter

### 2018-07-24 paper/paper.tex
fixing \lang

--- 2018-07-24 paper/paper.tex
@@
-\documentclass[review=true,acmlarge]{acmart}
+\documentclass[acmlarge]{acmart}
 
@@
 
-\newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
-\newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
-\newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
-\newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
+%% \newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
+%% \newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
+%% \newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
+%% \newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
 \newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
@@
 (define alice-label (let-label l (lambda (x) (= x alice)) l))
-(define x (fac alice-label 1 0))
+(define x (facet alice-label 1 0))
 (let ([alice-label (let-label l (lambda (x) true) l)]) |\label{lineno:alicelab}|
@@
 \begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=other,numbers=none]
-(fac l true (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
+(facet l true (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
 \end{lstlisting}
@@
 \begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=racets]
-(define-syntax-rule (fac l e1 e2)
+(define-syntax-rule (facet l e1 e2)
   (cond
@@
 (define p1board
-  (box (fac p1l
+  (box (facet p1l
             (add-pieces (makeboard) '(1 2 ldots))

### 2018-07-24 paper/paper.tex

@@
 counter. Our implementation uses Racket's parameters, though other
-mechanisms (such as continuation marks~\cite{Clements:2001}, to which parameters
+mechanisms (such as continuation marks~\cite{clements2001modeling}, to which parameters
 macro-expand) can also be used. \racets defines the parameter

### 2018-09-07 paper/paper.tex
fix some typos

@@
 relatively foundational linguistic changes required to enable faceted
-execution have hindered implementations thusfar. Dynamic generation
+execution have hindered implementations thus far. Dynamic generation
 of first-class security labels, tracking an arbitrary number of
@@
 
-To introduce faceted execution more concretely, we present the implementation
+To introduce faceted execution more concretely, we present our implementation
 of Battleship, a small guessing game, in \racets (this section presents a
@@
 argument and a possibly-faceted value to observe. After applying the
-policy its argument, we produce the value \bmth{v^{\pm}} and descend
+policy to its argument, we produce the value \bmth{v^{\pm}} and descend
 down the facet until reaching either a base value or finding the
@@
 programs emphasize purity while languages such as
-JavaScript (the original target of faceted execution) does not, so much
+JavaScript (the original target of faceted execution) do not, so much
 of the machinery for faceted execution's effect on the store is less

### 2018-09-11 paper/paper.tex
Adding changes for camera-ready

@@
 creating policies and faceting secure data with those
-policies. \racets also extends several core forms in Racket to work
+policies. \racets also rewrites several core forms in Racket to work
 with faceted values (our implementation is detailed in
-Section~\ref{sec:implementation}). We have used \racets to implement a
+Section~\ref{sec:implementation}). For example, function application
+must be treated specially to work with faceted values.
+We have used \racets to implement a
 small server-based board-game (detailed in Sections~\ref{sec:overview}
@@
 boards), it is written without any special machinery to maintain the
-secrecy of \code{board}. Protecting data {w.r.t.} policies is instead handled
-automatically and implicitly by a runtime monitor.
+secrecy of \code{board}. For example, nothing in \code{mark-hit}
+prevents Bob from using \code{mark-hit} on Alice's board, but faceted
+execution would ensure that if Bob tried to do this, he would always
+see the result \code{false}. Protecting data {w.r.t.} policies is
+instead handled automatically and implicitly by a runtime monitor.
 When Alice and Bob want to play a game, they both create a
-\emph{label} to protect their data. A label is unique id mapped to a policy predicate
-that takes a key (e.g., the current user's name) and returns true or false to indicate
-permission for the label. Alice's label is used to annotate the data she wants
-to be kept secret. Supposing Alice chooses to be player 1, she may use the
+\emph{label} to protect their data. A label is unique id mapped to a
+policy predicate that takes a key (e.g., the current user's name) and
+returns true or false to indicate permission for the label. Alice's
+label is used to annotate the data she wants to be kept
+secret. Supposing Alice chooses to be player 1, she may use the
 following label:
@@
           \begin{array}{rcrcl}
+            \fcol{\ell} & \fcol{\in} & \fcol{\text{label}} & \fcol{=} & \fcol{\ldots} \\
             \blue{\alpha} & \blue{\in} & \blue{\text{addr}} & \blue{=} & \blue{\ldots} \\
@@
             \fcol{b} & \fcol{\in} & \fcol{\text{branch}} & \fcol{::=} & \fcol{+ \ell \mid - \ell} \\
-            \fcol{pc} & \fcol{\in} & \fcol{\text{PC}} & \fcol{=} & \fcol{\wp(\text{branch})} \\
+            \fcol{pc} & \fcol{\in} & \fcol{\text{PC}} & \fcol{=} & \fcol{\{S \in \wp(\text{branch}) \mid \forall \ell. \{+\ell,-\ell\} \not\subseteq S\}} \\
             \blue{\rho} & \blue{\in} & \blue{\text{env}} & \blue{=} & \blue{\text{var} \rightharpoonup v}\\
@@
            \alpha \not\in dom(\sigma') \and \sigma'' = \sigma' [\alpha \mapsto \langle \lambda x. ~ e, \rho' \rangle] \\\\
-           e_2, \rho [ \ell \mapsto \alpha ], \sigma'' \Downarrow_{pc}^E \sigma''', v}
-          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
+           e_2, \rho [ x \mapsto \alpha ], \sigma'' \Downarrow_{pc}^E \sigma''', v}
+          {(\code{let-label} ~ x ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v}}
           & 
@@
           \inferrule[\textsc{App-Split}]
-          {\{+\ell, -\ell\} \cap pc = \varnothing \and
-            (v^+ ~ v), \rho, \sigma \Downarrow_{pc \cup \{+\ell\}}^A \sigma', {v^+}' \\\\
+           {(v^+ ~ v), \rho, \sigma \Downarrow_{pc \cup \{+\ell\}}^A \sigma', {v^+}' \and
+            {\{+\ell, -\ell\} \cap pc = \varnothing} \\\\
             (v^- ~ v), \rho, \sigma' \Downarrow_{pc \cup \{-\ell\}}^A \sigma'', {v^-}' \and
@@
 similar to the standard implementation of boxes, but employ several
-meta-functions to do their work. This is because box creation, reads,
-and writes may occur within a privileged context, and care must be
-taken to form facets when \rmth{pc} is nonempty. To understand why,
-consider the following example\footnote{Our formal semantics elides
-  \code{if}, though it may be obtained via a Church encoding if
-  desired as in Austin et al.\cite{Austin:2012}. Our implementation
-  includes \code{if} but not other constructs such as \code{cond}}:
+meta-functions to do their work (As they are largely similar to those
+in~\cite{Austin:2012}, we only detail $write$ here). This is because
+box creation, reads, and writes may occur within a privileged context,
+and care must be taken to form facets when \rmth{pc} is nonempty. To
+understand why, consider the following example\footnote{Our formal
+  semantics elides \code{if}, though it may be obtained via a Church
+  encoding if desired as in Austin et al.\cite{Austin:2012}. Our
+  implementation includes \code{if} but not other constructs such as
+  \code{cond}}:
 
@@
 \begin{lstlisting}[language=Racket,escapeinside={<@}{@>},name=other,numbers=none]
-(facet l true (error ''this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>''))
+(facet l true (error "this shouldn't get evaluated if <@\bmth{+\ell \in pc}@>"))
 \end{lstlisting}
@@
 consider the case under which a facet is used when an address is
-expected.
+expected. In our current implementation, nothing prevents programmers
+from misusing (or forgetting to use) our custom \code{box} and
+\code{unbox} forms. We leave this to future work.
 
@@
   \subfloat[]{%
-    \includegraphics[height=1.1in]{a.png}%
+    \includegraphics[height=2in]{a.png}%
     \label{fig:player1}%
@@
   \subfloat[]{%
-    \includegraphics[height=1.1in]{b.png}%
+    \includegraphics[height=2in]{b.png}%
     \label{fig:player1player2}%
@@
   \subfloat[]{%
-    \includegraphics[height=1.1in]{d.png}%
+    \includegraphics[height=2in]{d.png}%
     \label{fig:player1afterstrike}%
@@
 \begin{lstlisting}[language=Racket,escapechar=|,name=case]
+(define mkpol
+  (lambda (player-name)
+    (let-label l (lambda (x) (equal? x player-name)) l)))
+
 (define p1l (mkpol "player1"))
@@
 including security type systems and blame (to track which module
-violated the privacy policy).
+violated the privacy policy). We speculate that we may be able to
+piggy-back on top of Racket's existing contract system, and leave this
+to future work.
 
@@
 and variants of \code{LIO} that extend its
-power to arbitrary monad transformers~\cite{james}. We believe that it
-would be possible to implement a variant of our technique that would
-give similar insights to programs using \code{LIO}, though much of the
-interesting machinery for handling state may be unnecessary.
+power to arbitrary monad transformers~\cite{james}.
 
